---
title: "Altmetric_actual_mentions"
author: "Ana Macanovic"
date: "2024-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
```
Load the packages:
```{r message=TRUE, warning=TRUE}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", "PerformanceAnalytics",
                      "tidyverse", "RPostgres", "lubridate", "psych",
                      "digest", "DBI", "RODBC", "odbc", "gridExtra",
                      "panelr", "skimr", "foreach", "vegan",
                      "doParallel")
groundhog.library(packages_to_load, date = "2023-12-01")

# load the helper function file
source("helper_functions.R")
```

Connect to the database:
```{r}
# fill in own credentials
port <- 
user <- ""
password <- ""
database_name <- ""

con <- dbConnect(Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)

con # Checks connection is working
```


Load the professor profiles:
```{r message = F, warning = F}
narcis_prof_info <- dbReadTable(con, "narcis_prof_info")
prof_gender <- dbReadTable(con, "gender_table")
```


Load the prof-publication matching and the attention info:
```{r}
#prof - pub matching
oa_prof_pub_matching <- dbReadTable(con, "oa_prof_pub_match")
attention_news <- dbReadTable(con, "altmetric_pub_att_news")
attention_blogs <- dbReadTable(con, "altmetric_pub_att_blogs")
```

Match attention to profile_ids and first/last names of our professors:
```{r}
attention_news <- merge(attention_news,
                        oa_prof_pub_matching[c("id", "profile_id")],
                        by = "id",
                        all.x = TRUE)

attention_news <- merge(attention_news,
                        narcis_prof_info[c("profile_id", "last", "first")],
                        by = "profile_id",
                        all.x = TRUE)
```

Now, get the full texts:
```{r}
attention_news_full <- dbReadTable(con, "pub_att_news_full_text")

attention_news_full_filt <- filter(attention_news_full,
                                   response == 200)

```

Merge professor info with full text mentions:
```{r}
attention_news_full_filt <- merge(attention_news_full_filt,
                                  attention_news[c("profile_id", "id", "last", "first", "url", "posted_on")],
                                  by = "url")

attention_news_full_filt$first_last <- paste(attention_news_full_filt$first, attention_news_full_filt$last)

attention_news_full_filt <- merge(attention_news_full_filt,
                                  prof_gender[c("profile_id", "inferred_gender")])
```

Seek author's last names in the full text:
```{r}
attention_news_full_filt$name_mention <- str_detect(tolower(attention_news_full_filt$content), paste0("\\b", attention_news_full_filt$last, "\\b"))
```


Link to professor fields:
```{r}
oa_pubs_topics <- dbReadTable(con, "oa_pubs_topics")

oa_pubs_topics <- merge(oa_prof_pub_matching,
                        oa_pubs_topics,
                        by = "id",
                        all.x = TRUE)

prof_total_field <- oa_pubs_topics %>%
  group_by(profile_id, field_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

prof_total_field <- prof_total_field %>% 
  mutate(total_field = case_match(
    field_display_name,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))

attention_news_full_filt <- merge(attention_news_full_filt,
                                  prof_total_field,
                                  by = "profile_id",
                                  all.x = TRUE)


```

Get shares of mentions of papers that include professor's names per gender:
```{r}
gender_mentions_overall <- attention_news_full_filt %>%
  group_by(inferred_gender)%>%
  summarise(n_mentions = sum(name_mention == TRUE,na.rm = TRUE),
            n_all = n())%>%
  mutate(share_mentions = n_mentions / n_all)
```

Is this difference statistically signficant? Yes, it is.
```{r}
prop.test(x = gender_mentions_overall$n_mentions, n = gender_mentions_overall$n_all)
```

Per gender and field?
```{r}
gender_mentions_field <- attention_news_full_filt %>%
  group_by(inferred_gender, total_field)%>%
  summarise(n_mentions = sum(name_mention == TRUE,na.rm = TRUE),
            n_all = n())%>%
  mutate(share_mentions = n_mentions / n_all)

gender_mentions_field
```
Per field, get the proportion comparisons:
```{r}
fields <- unique(gender_mentions_field$total_field)

proportions_field <- as.data.frame(matrix(ncol = 2, nrow = 0))

for (field in fields){
  select <- filter(gender_mentions_field, total_field == as.symbol(field))
  test <- round(prop.test(x = select$n_mentions, n = select$n_all)$p.value, 5)
  proportions_field <- rbind(proportions_field,
                             cbind(field, test))
}

proportions_field
```

```{r}
# get a year from the "posted on" string
attention_news_full_filt$year <- year(as_date(attention_news_full_filt$posted_on))


prof_year_attention_news <- attention_news_full_filt %>%
  group_by(profile_id, year)%>%
  summarise(attn_news_by = n())%>%
  arrange(profile_id, year) %>%
  mutate(attn_news_by_total = cumsum(attn_news_by)) %>%
  arrange(profile_id, year)

prof_year_attention_news_l <- prof_year_attention_news 
colnames(prof_year_attention_news_l)[3:4] <- paste0(colnames(prof_year_attention_news_l)[3:4], "_l")

prof_year_attention_news_l <- prof_year_attention_news_l %>%
  arrange(year) %>%
  group_by(profile_id) %>%
  mutate_at(vars(contains('_l')), lag)%>%
  arrange(profile_id, year)

prof_year_attention_news_merge <- merge(prof_year_attention_news,
                                        prof_year_attention_news_l,
                                        by = c("profile_id", "year"))

colnames(prof_year_attention_news_merge)[-c(1:2)] <- paste0(colnames(prof_year_attention_news_merge)[-c(1:2)], "_name")
  
```

Merge with the prof panel:

```{r}
prof_panel <- read_csv("panel_datasets/prof_year_p_c_g_a_t_l_l_18_3.csv")
prof_panel_coa <- read_csv("panel_datasets/prof_panel_combined_no_lexis_19_3.csv")

# combine the two, since the latter mixes nexis data
lexis_data <- prof_panel %>%
  select(profile_id, year, contains("lexis"))

prof_panel_coa <- merge(prof_panel_coa,
                        lexis_data,
                        by= c("profile_id", "year"))

```

Merge the attention:
```{r}
prof_year_p_c_g_a <- merge(prof_panel_coa,
                           prof_year_attention_news_merge,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

# determine actual NAs
prof_year_p_c_g_a$attn_news_by_name <- ifelse((is.na(prof_year_p_c_g_a$attn_news_by_name) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_news_by_name)

prof_year_p_c_g_a$attn_news_by_total_name <- ifelse((is.na(prof_year_p_c_g_a$attn_news_by_total_name) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_news_by_total_name)

prof_year_p_c_g_a$attn_news_by_l_name <- ifelse((is.na(prof_year_p_c_g_a$attn_news_by_l_name) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_news_by_l_name)

prof_year_p_c_g_a$prof_tot_coa_attn_news_by_total_l <- ifelse((is.na(prof_year_p_c_g_a$prof_tot_coa_attn_news_by_total_l) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$prof_tot_coa_attn_news_by_total_l)

# fill
prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  group_by(profile_id)%>%
  fill(attn_news_by_total_name)

prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  group_by(profile_id)%>%
  fill(prof_tot_coa_attn_news_by_total_l)
```


```{r}

# recode the fields
prof_year_p_c_g_a <- prof_year_p_c_g_a %>% 
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))

prof_year_p_c_g_a <- prof_year_p_c_g_a %>% 
  mutate(general_field_yearly = case_match(
    yearly_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))
```
 
 
Rename the columns neatly:
```{r}
prof_panel_tidy <- prof_year_p_c_g_a %>%
  select(-c(cited_by_before_2012, cited_by_total_oa, cited_by_total_oa_l, dupl, dupl_l, 
           coa_cited_by_before_2012, coa_count_pubs_before_2012, coa_cited_by_before_2012_l,
           coa_count_pubs_before_2012, prof_tot_count_pubs_total_oa, prof_tot_cited_by_total_oa,
           prof_tot_cited_by_before_2012, prof_tot_count_pubs_before_2012 ))%>%
  rename(
    online_news = attn_news_by,
    online_news_total = attn_news_by_total,
    online_news_l = attn_news_by_l,
    online_news_total_l = attn_news_by_total_l,
    online_news_name = attn_news_by_name,
    online_news_name_total = attn_news_by_total_name,
    online_news_name_l = attn_news_by_l_name,
    online_news_name_total_l = prof_tot_coa_attn_news_by_total_l,
    blogs = attn_blogs_by,
    blogs_total = attn_blogs_by_total,
    blogs_l = attn_blogs_by_l,
    blogs_total_l = attn_blogs_by_total_l,
    twitter = attn_twitter_by,
    twitter_total = attn_twitter_by_total,
    twitter_l = attn_twitter_by_l,
    twitter_total_l = attn_twitter_by_total_l,
    grant_veni = veni,
    grant_veni_l = veni_l,
    grant_vidi = vidi,
    grant_vidi_l = vidi_l,    
    grant_vici = vici,
    grant_vici_l = vici_l,
    grant_stevin = stevin,
    grant_stevin_l = stevin_l,
    grant_spinoza = spinoza,
    grant_spinoza_l = spinoza_l,
    grant_starting = starting,
    grant_starting_l = starting_l,
    grant_advanced = advanced,
    grant_advanced_l = advanced_l,
    grant_consolidator = consolidator,
    grant_consolidator_l = consolidator_l,
    grant_synergy = synergy,
    grant_synergy_l = synergy_l,
    coa_online_news = coa_attn_news_by,
    coa_blogs = coa_attn_blog_by,
    coa_twitter = coa_attn_twitter_by,
    coa_online_news_total = coa_attn_news_by_total,
    coa_blogs_total = coa_attn_blog_by_total,
    coa_twitter_total = coa_attn_twitter_by_total,
    coa_online_news_l = coa_attn_news_by_l,
    coa_blogs_l = coa_attn_blog_by_l,
    coa_twitter_l = coa_attn_twitter_by_l,
    coa_online_news_total_l = coa_attn_news_by_total_l,
    coa_blogs_total_l = coa_attn_blog_by_total_l,
    coa_twitter_total_l = coa_attn_twitter_by_total_l,
    coa_tot_count_pubs = prof_tot_count_pubs, 
    coa_tot_cited_by = prof_tot_cited_by,
    coa_tot_count_pubs_total = prof_tot_count_pubs_total_all,
    coa_tot_cited_by_total = prof_tot_cited_by_total_all,
    coa_tot_online_news = prof_tot_coa_attn_news_by,
    coa_tot_blogs = prof_tot_coa_attn_blog_by,
    coa_tot_twitter = prof_tot_coa_attn_twitter_by,
    coa_tot_online_news_total = prof_tot_coa_attn_news_by_total,
    coa_tot_blogs_total = prof_tot_coa_attn_blog_by_total,
    coa_tot_twitter_total = prof_tot_coa_attn_twitter_by_total,
    coa_tot_unique_m = prof_tot_unique_coa_m,
    coa_tot_unique_w = prof_tot_unique_coa_w,
    coa_tot_unique_u = prof_tot_unique_coa_u,
    coa_tot_count_pubs_l = prof_tot_count_pubs_l, 
    coa_tot_cited_by_l = prof_tot_cited_by_l,
    coa_tot_count_pubs_total_l = prof_tot_count_pubs_total_all_l,
    coa_tot_cited_by_total_l = prof_tot_cited_by_total_all_l,
    coa_tot_online_news_l = prof_tot_coa_attn_news_by_l,
    coa_tot_blogs_l = prof_tot_coa_attn_blog_by_l,
    coa_tot_twitter_l = prof_tot_coa_attn_twitter_by_l,
    coa_tot_online_news_total_l = prof_tot_coa_attn_news_by_total_l,
    coa_tot_blogs_total_l = prof_tot_coa_attn_blog_by_total_l,
    coa_tot_twitter_total_l = prof_tot_coa_attn_twitter_by_total_l,
    coa_tot_unique_m_l = prof_tot_unique_coa_m_l,
    coa_tot_unique_w_l = prof_tot_unique_coa_w_l,
    coa_tot_unique_u_l = prof_tot_unique_coa_u_l,
    news_national = lexis_national,
    news_regional = lexis_regional,
    news_intl = lexis_intl,
    news = lexis_all,
    news_national_total = lexis_national_total,
    news_regional_total = lexis_regional_total,
    news_intl_total = lexis_intl_total,
    news_total = lexis_all_total,
    news_national_l = lexis_national_l,
    news_regional_l = lexis_regional_l,
    news_intl_l = lexis_intl_l,
    news_l = lexis_all_l,
    news_national_total_l = lexis_national_total_l,
    news_regional_total_l = lexis_regional_total_l,
    news_intl_total_l = lexis_intl_total_l,
    news_total_l = lexis_all_total_l)
```
 

Select relevant columns and tidy everything up:
```{r}
prof_panel_tidy <- prof_panel_tidy %>%
  # but not 2024
  filter(year < 2024 & !is.na(year))

# tidy up mentions
prof_panel_tidy$online_news_blogs <- prof_panel_tidy$online_news + prof_panel_tidy$blogs
prof_panel_tidy$online_news_blogs_l <- prof_panel_tidy$online_news_l + prof_panel_tidy$blogs_l
prof_panel_tidy$online_news_blogs_total_l <- prof_panel_tidy$online_news_total_l + prof_panel_tidy$blogs_total_l

# coauthors this year
prof_panel_tidy$coa_online_news_blogs <- prof_panel_tidy$coa_online_news + prof_panel_tidy$coa_blogs
prof_panel_tidy$coa_online_news_blogs_l <- prof_panel_tidy$coa_online_news_l + prof_panel_tidy$coa_blogs_l
prof_panel_tidy$coa_online_news_blogs_total <- prof_panel_tidy$coa_online_news_total + prof_panel_tidy$coa_blogs_total
prof_panel_tidy$coa_online_news_blogs_total_l <- prof_panel_tidy$coa_online_news_total_l + prof_panel_tidy$coa_blogs_total_l

# all coauthors up until now
prof_panel_tidy$coa_tot_online_news_blogs <- prof_panel_tidy$coa_tot_online_news + prof_panel_tidy$coa_tot_blogs
prof_panel_tidy$coa_tot_online_news_blogs_l <- prof_panel_tidy$coa_tot_online_news_l + prof_panel_tidy$coa_tot_blogs_l
prof_panel_tidy$coa_tot_online_news_blogs_total <- prof_panel_tidy$coa_tot_online_news_total + prof_panel_tidy$coa_tot_blogs_total
prof_panel_tidy$coa_tot_online_news_blogs_total_l <- prof_panel_tidy$coa_tot_online_news_total_l + prof_panel_tidy$coa_tot_blogs_total_l

# get groups per years since entry
prof_panel_tidy$entry_batch <- cut(prof_panel_tidy$years_since_first_pub, breaks = seq(0, 50, by=10))
prof_panel_tidy$years_since_entry <- paste("up to", str_remove(str_split_i(as.character(prof_panel_tidy$entry_batch), ",", 2),"]"))
```

Alternatively, leave only those professors for whom we actually have lexis data:
```{r warning = F, message = F}
# ones we collected before 20.3. in the morning 
lexis_info <- file.info(list.files(path = "../lexis_crawl/downloads/zipfiles",
                                   pattern="*.zip",
                                   full.names = T))
lexis_rel_list <- filter(lexis_info,
                         mtime <= "2024-03-20 8:55:00")

lexis_rel_list$profile_id <- str_remove(str_remove(rownames(lexis_rel_list), "../lexis_crawl/downloads/zipfiles/"), ".zip")

# minus ones that are incomplete
missing_indices <- read_csv("../lexis_crawl/missing_indices.csv")

lexis_list <- filter(lexis_rel_list, ! profile_id %in% missing_indices$profile_id)

prof_panel_filter <- filter(prof_panel_tidy,
                            str_remove(profile_id, "https://www.narcis.nl/person/RecordID/") %in% lexis_list$profile_id)
```

Write this out:
```{r}
write_csv(prof_panel_filter, "panel_datasets/full_panel_lexis_name_altm_26_3_3655_prof.csv")
```

