---
title: "Untitled"
author: "Ana Macanovic"
date: "2024-03-04"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message=FALSE)
```


Load the packages:
```{r message=  F, warning = F, eval = T, echo=T}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "tidyverse", "RPostgres", "lubridate", "psych",
                      "gridExtra",
                      "panelr", "skimr",
                      "lmtest", "sandwich")
groundhog.library(packages_to_load, date = "2023-12-01")

```

Load the panel and tidying it up:
```{r warning = F, message = F, echo=T}
prof_year_p_c_g_a_t <-  read_csv("panel_datasets/prof_year_p_c_g_a_t.csv")
prof_year_p_c_g_a_t_l <-  read_csv("panel_datasets/prof_year_p_c_g_a_t_l.csv")

prof_year_p_c_g_a_t_l$all_mentions <- prof_year_p_c_g_a_t_l$attn_news_by + prof_year_p_c_g_a_t_l$attn_blogs_by + prof_year_p_c_g_a_t_l$attn_twitter_by
prof_year_p_c_g_a_t_l$all_mentions_total <- prof_year_p_c_g_a_t_l$attn_news_by_total + prof_year_p_c_g_a_t_l$attn_blogs_by_total + prof_year_p_c_g_a_t_l$attn_twitter_by_total
```
 
Get attention percentiles per year and per year and field.(code is hidden for clarity)
```{r}
fame_distributions_y <- prof_year_p_c_g_a_t_l %>%
  filter(year >= 2011 & !is.na(overall_field))%>%
  group_by(year) %>%
  summarize(n = n(),
            quant50_att = quantile(all_mentions, probs = 0.5, na.rm = TRUE),
            quant75_att = quantile(all_mentions, probs = 0.75, na.rm = TRUE),
            quant90_att = quantile(all_mentions, probs = 0.9, na.rm = TRUE),
            quant95_att = quantile(all_mentions, probs = 0.95, na.rm = TRUE),
            quant50_pubs = quantile(count_pubs, probs = 0.5, na.rm = TRUE),
            quant75_pubs = quantile(count_pubs, probs = 0.75, na.rm = TRUE),
            quant90_pubs = quantile(count_pubs, probs = 0.9, na.rm = TRUE),
            quant95_pubs = quantile(count_pubs, probs = 0.95, na.rm = TRUE),
            quant50_cits = quantile(cited_by, probs = 0.5, na.rm = TRUE),
            quant75_cits = quantile(cited_by, probs = 0.75, na.rm = TRUE),
            quant90_cits = quantile(cited_by, probs = 0.9, na.rm = TRUE),
            quant95_cits = quantile(cited_by, probs = 0.95, na.rm = TRUE))

fame_distributions_y_f <- prof_year_p_c_g_a_t_l %>%
  filter(year >= 2011 & !is.na(overall_field))%>%
  group_by(year, overall_field) %>%
  summarize(n = n(),
            quant50_att = quantile(all_mentions, probs = 0.5, na.rm = TRUE),
            quant75_att = quantile(all_mentions, probs = 0.75, na.rm = TRUE),
            quant90_att = quantile(all_mentions, probs = 0.9, na.rm = TRUE),
            quant95_att = quantile(all_mentions, probs = 0.95, na.rm = TRUE),
            quant50_pubs = quantile(count_pubs, probs = 0.5, na.rm = TRUE),
            quant75_pubs = quantile(count_pubs, probs = 0.75, na.rm = TRUE),
            quant90_pubs = quantile(count_pubs, probs = 0.9, na.rm = TRUE),
            quant95_pubs = quantile(count_pubs, probs = 0.95, na.rm = TRUE),
            quant50_cits = quantile(cited_by, probs = 0.5, na.rm = TRUE),
            quant75_cits = quantile(cited_by, probs = 0.75, na.rm = TRUE),
            quant90_cits = quantile(cited_by, probs = 0.9, na.rm = TRUE),
            quant95_cits = quantile(cited_by, probs = 0.95, na.rm = TRUE))

fame_distributions_y_tot <- prof_year_p_c_g_a_t_l %>%
  filter(year >= 2011 & !is.na(overall_field))%>%
  group_by(year) %>%
  summarize(n = n(),
            quant50_att = quantile(all_mentions_total, probs = 0.5, na.rm = TRUE),
            quant75_att = quantile(all_mentions_total, probs = 0.75, na.rm = TRUE),
            quant90_att = quantile(all_mentions_total, probs = 0.9, na.rm = TRUE),
            quant95_att = quantile(all_mentions_total, probs = 0.95, na.rm = TRUE),
            quant50_pubs = quantile(count_pubs_total, probs = 0.5, na.rm = TRUE),
            quant75_pubs = quantile(count_pubs_total, probs = 0.75, na.rm = TRUE),
            quant90_pubs = quantile(count_pubs_total, probs = 0.9, na.rm = TRUE),
            quant95_pubs = quantile(count_pubs_total, probs = 0.95, na.rm = TRUE),
            quant50_cits = quantile(cited_by_total_all, probs = 0.5, na.rm = TRUE),
            quant75_cits = quantile(cited_by_total_all, probs = 0.75, na.rm = TRUE),
            quant90_cits = quantile(cited_by_total_all, probs = 0.9, na.rm = TRUE),
            quant95_cits = quantile(cited_by_total_all, probs = 0.95, na.rm = TRUE))

fame_distributions_y_f_tot <- prof_year_p_c_g_a_t_l %>%
  filter(year >= 2011 & !is.na(overall_field))%>%
  group_by(year, overall_field) %>%
  summarize(n = n(),
            quant50_att = quantile(all_mentions_total, probs = 0.5, na.rm = TRUE),
            quant75_att = quantile(all_mentions_total, probs = 0.75, na.rm = TRUE),
            quant90_att = quantile(all_mentions_total, probs = 0.9, na.rm = TRUE),
            quant95_att = quantile(all_mentions_total, probs = 0.95, na.rm = TRUE),
            quant50_pubs = quantile(count_pubs_total, probs = 0.5, na.rm = TRUE),
            quant75_pubs = quantile(count_pubs_total, probs = 0.75, na.rm = TRUE),
            quant90_pubs = quantile(count_pubs_total, probs = 0.9, na.rm = TRUE),
            quant95_pubs = quantile(count_pubs_total, probs = 0.95, na.rm = TRUE),
            quant50_cits = quantile(cited_by_total_all, probs = 0.5, na.rm = TRUE),
            quant75_cits = quantile(cited_by_total_all, probs = 0.75, na.rm = TRUE),
            quant90_cits = quantile(cited_by_total_all, probs = 0.9, na.rm = TRUE),
            quant95_cits = quantile(cited_by_total_all, probs = 0.95, na.rm = TRUE))

```

Match profs with percentiles.
```{r}
prof_percentile_matching <- prof_year_p_c_g_a_t_l %>%
  filter(year > 2011)%>%
  select(profile_id, year, inferred_gender, overall_field, attn_news_by, count_pubs,
         count_pubs_total, cited_by, cited_by_total_all,
         attn_news_by_total, attn_blogs_by, attn_blogs_by_total, attn_twitter_by,
         attn_twitter_by_total, all_mentions, all_mentions_total)

prof_percentile_matching <- merge(prof_percentile_matching,
                                  fame_distributions_y,
                                  by = "year",
                                  all.x = TRUE)
prof_percentile_matching <- prof_percentile_matching %>%
  mutate(per_50_year_att = if_else(all_mentions >= quant50_att, 1, 0),
         per_75_year_att = if_else(all_mentions >= quant75_att, 1, 0),
         per_90_year_att = if_else(all_mentions >= quant90_att, 1, 0),
         per_95_year_att = if_else(all_mentions >= quant95_att, 1, 0),
         per_50_year_pubs = if_else(count_pubs >= quant50_pubs, 1, 0),
         per_75_year_pubs = if_else(count_pubs >= quant75_pubs, 1, 0),
         per_90_year_pubs = if_else(count_pubs >= quant90_pubs, 1, 0),
         per_95_year_pubs = if_else(count_pubs >= quant95_pubs, 1, 0),
         per_50_year_cits = if_else(cited_by >= quant50_cits, 1, 0),
         per_75_year_cits = if_else(cited_by >= quant75_cits, 1, 0),
         per_90_year_cits = if_else(cited_by >= quant90_cits, 1, 0),
         per_95_year_cits = if_else(cited_by >= quant95_cits, 1, 0))%>%
  select(!(quant50_att:quant95_cits))

prof_percentile_matching <- merge(prof_percentile_matching,
                                  fame_distributions_y_f,
                                  by = c("year", "overall_field"),
                                  all.x = TRUE)

prof_percentile_matching <- prof_percentile_matching %>%
  mutate(per_50_year_field_att = if_else(all_mentions >= quant50_att, 1, 0),
         per_75_year_field_att = if_else(all_mentions >= quant75_att, 1, 0),
         per_90_year_field_att = if_else(all_mentions >= quant90_att, 1, 0),
         per_95_year_field_att = if_else(all_mentions >= quant95_att, 1, 0),
         per_50_year_field_pubs = if_else(count_pubs >= quant50_pubs, 1, 0),
         per_75_year_field_pubs = if_else(count_pubs >= quant75_pubs, 1, 0),
         per_90_year_field_pubs = if_else(count_pubs >= quant90_pubs, 1, 0),
         per_95_year_field_pubs = if_else(count_pubs >= quant95_pubs, 1, 0),
         per_50_year_field_cits = if_else(cited_by >= quant50_cits, 1, 0),
         per_75_year_field_cits = if_else(cited_by >= quant75_cits, 1, 0),
         per_90_year_field_cits = if_else(cited_by >= quant90_cits, 1, 0),
         per_95_year_field_cits = if_else(cited_by >= quant95_cits, 1, 0))%>%
  select(!(quant50_att:quant95_cits))
```

# Gender structure overall
This explores the share of publications, citations, and attention of women
out of the total number of publications, citations, and attention.

Get fame gender breakdown per year. [code hidden]
```{r}
year_breakdown_att <- prof_percentile_matching %>%
  group_by(year)%>%
  summarise(n_att = sum(all_mentions),
            w_att = sum(all_mentions[inferred_gender == "w"]))%>%
  mutate(w_att = w_att/n_att*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_att <- prof_percentile_matching %>%
  filter(!is.na(overall_field))%>%
  group_by(year, overall_field)%>%
  summarise(n_att = sum(all_mentions),
            w_att = sum(all_mentions[inferred_gender == "w"]))%>%
  mutate(w_att = w_att/n_att*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 
 year_breakdown_pubs <- prof_percentile_matching %>%
  group_by(year)%>%
  summarise(n_pubs = sum(count_pubs),
            w_pubs = sum(count_pubs[inferred_gender == "w"]))%>%
  mutate(w_pubs = w_pubs/n_pubs*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_pubs <- prof_percentile_matching %>%
  filter(!is.na(overall_field))%>%
  group_by(year, overall_field)%>%
  summarise(n_pubs = sum(count_pubs),
            w_pubs = sum(count_pubs[inferred_gender == "w"]))%>%
  mutate(w_pubs = w_pubs/n_pubs*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 year_breakdown_cits <- prof_percentile_matching %>%
   filter(year >= 2012)%>%
   group_by(year)%>%
   summarise(n_cits = sum(cited_by, na.rm = T),
             w_cits = sum(cited_by[inferred_gender == "w"],  na.rm = T)) %>%
   mutate(w_cits = w_cits/n_cits*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 year_breakdown_field_cits <- prof_percentile_matching %>%
   filter(year >= 2012)%>%
   filter(!is.na(overall_field))%>%
   group_by(year, overall_field)%>%
   summarise(n_cits = sum(cited_by, na.rm = T),
             w_cits = sum(cited_by[inferred_gender == "w"],  na.rm = T)) %>%
   mutate(w_cits = w_cits/n_cits*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 
 share_women_year <- prof_percentile_matching %>%
   group_by(year)%>%
   summarise(
     n = n(),
     w = sum(inferred_gender == "w")/n()*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 share_women_field_year <- prof_percentile_matching %>%
   filter(!is.na(overall_field))%>%
   group_by(year, overall_field)%>%
   summarise( n = n(),
              w = sum(inferred_gender == "w")/n()*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))

#put all data frames into list
merge_list_year <- list(share_women_year, 
                        year_breakdown_pubs, 
                        year_breakdown_cits,
                        year_breakdown_att)

merge_list_year_field <- list(share_women_field_year, 
                              year_breakdown_field_pubs, 
                              year_breakdown_field_cits,
                              year_breakdown_field_att)


year_breakdown <- merge_list_year %>%
  reduce(full_join,
         by = "year")

year_field_breakdown <- merge_list_year_field %>%
  reduce(left_join,
         by = c("year", "overall_field"))

```

Plot the shares of women per year:

```{r fig.width = 10}
year_breakdown$year <- as.factor(year_breakdown$year)

(plot_data_year <- year_breakdown %>%
    filter(year != "2024")%>%
    select(-contains("n"))%>%
    pivot_longer(!year, names_to = "type", values_to = "share_women") %>%
    ggplot(aes(color=type, y=share_women, x=year, group = type)) + 
    geom_line()+
    scale_color_hue(labels = c("Professors", "In all attention",
                                  "In all citations", "In all publication counts"))+
    labs(x = 'Year', y = "Share women", color = "")+
    theme_minimal())
```

Share of women per field:

```{r fig.width = 10}
year_field_breakdown$year <- as.factor(year_field_breakdown$year)
label_counts <- filter(year_field_breakdown,
                       year == 2013)
label_counts$label <- paste0(label_counts$overall_field, " (n = ", label_counts$n, ")")

year_field_breakdown <- year_field_breakdown %>% 
  mutate(overall_field_short = case_match(
    overall_field,
    "Agricultural and Biological Sciences"  ~ "Agri & Bio Sciences",
    "Arts and Humanities"  ~ "Arts & Humanities",
    "Biochemistry, Genetics and Molecular Biology" ~ "Biochem, Genetics & Mol Bio",
    "Business, Management and Accounting" ~ "Business, Mgmt & Acc",
    "Chemical Engineering" ~ "Chem Eng",
    "Chemistry" ~  "Chem",
    "Computer Science" ~ "Comp Sci",
    "Decision Sciences" ~ "Dec Sci",
    "Dentistry"  ~ "Dentistry",
    "Earth and Planetary Sciences" ~ "Earth & Planetary Sci",
    "Economics, Econometrics and Finance" ~"Econ & Finance",
    "Energy" ~  "Energy",      
    "Engineering" ~ "Engineering",
    "Environmental Science" ~ "Envir Sci",
    "Health Professions" ~ "Health Prof",
    "Immunology and Microbiology" ~  "Immunology & MicroBio",
    "Materials Science" ~ "Materials Sci",
    "Mathematics"  ~ "Math",
    "Medicine" ~ "Medicine",
    "Neuroscience" ~ "Neurosci",
    "Physics and Astronomy" ~ "Physics & Astro",
    "Psychology" ~ "Psychology",
    "Social Sciences"    ~ "Soc Sci"                         
  ))

year_field_breakdown <- year_field_breakdown %>% 
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))
    
labels <- year_field_breakdown %>% filter(year == 2023)%>%
  group_by(general_field) %>%
  summarise( n = sum(n))

labels$field_n_label <- paste0(labels$general_field, " (n = ", labels$n, ")")

year_field_breakdown <- merge(year_field_breakdown,
                              labels[c("general_field", "field_n_label")])

(plot_data_year_field <-  year_field_breakdown %>%
  filter(year != "2024")%>%
  select(-c(n, n_pubs, n_cits, n_att, overall_field_short))%>%
  group_by(year, field_n_label)%>%
  summarise(w = mean(w),
            w_att = mean(w_att),
            w_pubs = mean(w_pubs),
            w_cits = mean(w_cits))%>%
  pivot_longer(w:w_cits, names_to = "type", values_to = "share_women") %>%
    ggplot(aes(color=type, y=share_women, x=year, group = type)) + 
    geom_line()+
    facet_wrap(.~field_n_label, scales = "free")+
    scale_color_hue(labels = c("Professors", "In all attention",
                                  "In all citations", "In all publication counts"))+
    labs(x = 'Year', y = "Share women", color = "")+
    theme_minimal())

```



# Gender structure of top 25% by pubs, cits, and attention
This explores the share of women in the top 25% of scientists given their
yearly publications, citations, and attention.

Fame gender breakdown per year. [code hidden]
```{r}
year_breakdown_att <- prof_percentile_matching %>%
  group_by(year)%>%
  filter(per_75_year_field_att == 1)%>%
  summarise(n_att = n(),
            w_att = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_att <- prof_percentile_matching %>%
  filter(!is.na(overall_field) & per_75_year_field_att == 1)%>%
  group_by(year, overall_field)%>%
   summarise(n_att = n(),
            w_att = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 
 year_breakdown_pubs <- prof_percentile_matching %>%
  group_by(year)%>%
  filter(per_75_year_field_pubs == 1)%>%
  summarise(n_pubs = n(),
            w_pubs = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_pubs <- prof_percentile_matching %>%
  filter(!is.na(overall_field) & per_75_year_field_pubs == 1)%>%
  group_by(year, overall_field)%>%
   summarise(n_pubs = n(),
            w_pubs = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 year_breakdown_cits <- prof_percentile_matching %>%
  group_by(year)%>%
  filter(per_75_year_field_cits == 1)%>%
  summarise(n_cits = n(),
            w_cits = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_cits <- prof_percentile_matching %>%
  filter(!is.na(overall_field) & per_75_year_field_cits == 1)%>%
  group_by(year, overall_field)%>%
   summarise(n_cits = n(),
            w_cits = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 
 share_women_year <- prof_percentile_matching %>%
   group_by(year)%>%
   summarise(
     n = n(),
     w = sum(inferred_gender == "w")/n()*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 share_women_field_year <- prof_percentile_matching %>%
   filter(!is.na(overall_field))%>%
   group_by(year, overall_field)%>%
   summarise( n = n(),
              w = sum(inferred_gender == "w")/n()*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))

#put all data frames into list
merge_list_year <- list(share_women_year, 
                        year_breakdown_pubs, 
                        year_breakdown_cits,
                        year_breakdown_att)

merge_list_year_field <- list(share_women_field_year, 
                              year_breakdown_field_pubs, 
                              year_breakdown_field_cits,
                              year_breakdown_field_att)


year_breakdown <- merge_list_year %>%
  reduce(full_join,
         by = "year")

year_field_breakdown <- merge_list_year_field %>%
  reduce(left_join,
         by = c("year", "overall_field"))

```

Plot the shares of famous women (top 25% of pubs, citations, attention):

```{r fig.width = 10}
year_breakdown$year <- as.factor(year_breakdown$year)

((plot_data_year <- year_breakdown %>%
    filter(year != "2024")%>%
    select(-contains("n"))%>%
    pivot_longer(!year, names_to = "type", values_to = "share_women")%>%
    ggplot(aes(color=type, y=share_women, x=year, group = type)) + 
    geom_line()+
    scale_color_hue(labels = c("Professors", "In top 25% attention",
                                  "In top 25% citations", "In top 25% publication counts"))+
    labs(x = 'Year', y = "Share women", color = "")+
    theme_minimal()))
```

Do the same per field:

```{r fig.width = 10}
year_field_breakdown$year <- as.factor(year_field_breakdown$year)
label_counts <- filter(year_field_breakdown,
                       year == 2013)
label_counts$label <- paste0(label_counts$overall_field, " (n = ", label_counts$n, ")")

year_field_breakdown <- year_field_breakdown %>% 
  mutate(overall_field_short = case_match(
    overall_field,
    "Agricultural and Biological Sciences"  ~ "Agri & Bio Sciences",
    "Arts and Humanities"  ~ "Arts & Humanities",
    "Biochemistry, Genetics and Molecular Biology" ~ "Biochem, Genetics & Mol Bio",
    "Business, Management and Accounting" ~ "Business, Mgmt & Acc",
    "Chemical Engineering" ~ "Chem Eng",
    "Chemistry" ~  "Chem",
    "Computer Science" ~ "Comp Sci",
    "Decision Sciences" ~ "Dec Sci",
    "Dentistry"  ~ "Dentistry",
    "Earth and Planetary Sciences" ~ "Earth & Planetary Sci",
    "Economics, Econometrics and Finance" ~"Econ & Finance",
    "Energy" ~  "Energy",      
    "Engineering" ~ "Engineering",
    "Environmental Science" ~ "Envir Sci",
    "Health Professions" ~ "Health Prof",
    "Immunology and Microbiology" ~  "Immunology & MicroBio",
    "Materials Science" ~ "Materials Sci",
    "Mathematics"  ~ "Math",
    "Medicine" ~ "Medicine",
    "Neuroscience" ~ "Neurosci",
    "Physics and Astronomy" ~ "Physics & Astro",
    "Psychology" ~ "Psychology",
    "Social Sciences"    ~ "Soc Sci"                         
  ))

year_field_breakdown <- year_field_breakdown %>% 
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))
    
labels <- year_field_breakdown %>% filter(year == 2023)%>%
  group_by(general_field) %>%
  summarise( n = sum(n))

labels$field_n_label <- paste0(labels$general_field, " (n = ", labels$n, ")")

year_field_breakdown <- merge(year_field_breakdown,
                              labels[c("general_field", "field_n_label")])

(plot_data_year_field <-  year_field_breakdown %>%
  filter(year != "2024")%>%
  select(-c(n, n_pubs, n_cits, n_att, overall_field_short))%>%
  group_by(year, field_n_label)%>%
  summarise(w = mean(w),
            w_att = mean(w_att),
            w_pubs = mean(w_pubs),
            w_cits = mean(w_cits))%>%
  pivot_longer(w:w_cits, names_to = "type", values_to = "share_women") %>%
    ggplot(aes(color=type, y=share_women, x=year, group = type)) + 
    geom_line()+
    facet_wrap(.~field_n_label, scales = "free")+
    scale_color_hue(labels = c("Professors", "In top 25% attention",
                                  "In top 25% citations", "In top 25% publication counts"))+
    labs(x = 'Year', y = "Share women", color = "")+
    theme_minimal())

```


# Gender structure of top 5% by pubs, cits, and attention
This explores the share of women in the top 5% of scientists given their
yearly publications, citations, and attention.

Fame gender breakdown per year. [code hidden]
```{r}
year_breakdown_att <- prof_percentile_matching %>%
  group_by(year)%>%
  filter(per_95_year_field_att == 1)%>%
  summarise(n_att = n(),
            w_att = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_att <- prof_percentile_matching %>%
  filter(!is.na(overall_field) & per_95_year_field_att == 1)%>%
  group_by(year, overall_field)%>%
   summarise(n_att = n(),
            w_att = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 
 year_breakdown_pubs <- prof_percentile_matching %>%
  group_by(year)%>%
  filter(per_95_year_field_pubs == 1)%>%
  summarise(n_pubs = n(),
            w_pubs = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_pubs <- prof_percentile_matching %>%
  filter(!is.na(overall_field) & per_95_year_field_pubs == 1)%>%
  group_by(year, overall_field)%>%
   summarise(n_pubs = n(),
            w_pubs = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 year_breakdown_cits <- prof_percentile_matching %>%
  group_by(year)%>%
  filter(per_95_year_field_cits == 1)%>%
  summarise(n_cits = n(),
            w_cits = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))

 year_breakdown_field_cits <- prof_percentile_matching %>%
  filter(!is.na(overall_field) & per_95_year_field_cits == 1)%>%
  group_by(year, overall_field)%>%
   summarise(n_cits = n(),
            w_cits = sum(inferred_gender == "w")/n()*100)%>%
  mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 
 share_women_year <- prof_percentile_matching %>%
   group_by(year)%>%
   summarise(
     n = n(),
     w = sum(inferred_gender == "w")/n()*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))
 
 share_women_field_year <- prof_percentile_matching %>%
   filter(!is.na(overall_field))%>%
   group_by(year, overall_field)%>%
   summarise( n = n(),
              w = sum(inferred_gender == "w")/n()*100)%>%
   mutate(across(where(is.numeric), \(x) round(x, 2)))

#put all data frames into list
merge_list_year <- list(share_women_year, 
                        year_breakdown_pubs, 
                        year_breakdown_cits,
                        year_breakdown_att)

merge_list_year_field <- list(share_women_field_year, 
                              year_breakdown_field_pubs, 
                              year_breakdown_field_cits,
                              year_breakdown_field_att)


year_breakdown <- merge_list_year %>%
  reduce(full_join,
         by = "year")

year_field_breakdown <- merge_list_year_field %>%
  reduce(left_join,
         by = c("year", "overall_field"))

```

Plot the shares of famous women (top 5% of pubs, citations, attention):

```{r fig.width = 10}
year_breakdown$year <- as.factor(year_breakdown$year)

((plot_data_year <- year_breakdown %>%
    filter(year != "2024")%>%
    select(-contains("n"))%>%
    pivot_longer(!year, names_to = "type", values_to = "share_women")%>%
    ggplot(aes(color=type, y=share_women, x=year, group = type)) + 
    geom_line()+
    scale_color_hue(labels = c("Professors", "In top 5% attention",
                                  "In top 5% citations", "In top 5% publication counts"))+
    labs(x = 'Year', y = "Share women", color = "")+
    theme_minimal()))
```

Do the same per field:

```{r fig.width = 10}
year_field_breakdown$year <- as.factor(year_field_breakdown$year)
label_counts <- filter(year_field_breakdown,
                       year == 2013)
label_counts$label <- paste0(label_counts$overall_field, " (n = ", label_counts$n, ")")

year_field_breakdown <- year_field_breakdown %>% 
  mutate(overall_field_short = case_match(
    overall_field,
    "Agricultural and Biological Sciences"  ~ "Agri & Bio Sciences",
    "Arts and Humanities"  ~ "Arts & Humanities",
    "Biochemistry, Genetics and Molecular Biology" ~ "Biochem, Genetics & Mol Bio",
    "Business, Management and Accounting" ~ "Business, Mgmt & Acc",
    "Chemical Engineering" ~ "Chem Eng",
    "Chemistry" ~  "Chem",
    "Computer Science" ~ "Comp Sci",
    "Decision Sciences" ~ "Dec Sci",
    "Dentistry"  ~ "Dentistry",
    "Earth and Planetary Sciences" ~ "Earth & Planetary Sci",
    "Economics, Econometrics and Finance" ~"Econ & Finance",
    "Energy" ~  "Energy",      
    "Engineering" ~ "Engineering",
    "Environmental Science" ~ "Envir Sci",
    "Health Professions" ~ "Health Prof",
    "Immunology and Microbiology" ~  "Immunology & MicroBio",
    "Materials Science" ~ "Materials Sci",
    "Mathematics"  ~ "Math",
    "Medicine" ~ "Medicine",
    "Neuroscience" ~ "Neurosci",
    "Physics and Astronomy" ~ "Physics & Astro",
    "Psychology" ~ "Psychology",
    "Social Sciences"    ~ "Soc Sci"                         
  ))

year_field_breakdown <- year_field_breakdown %>% 
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))
    
labels <- year_field_breakdown %>% filter(year == 2023)%>%
  group_by(general_field) %>%
  summarise( n = sum(n))

labels$field_n_label <- paste0(labels$general_field, " (n = ", labels$n, ")")

year_field_breakdown <- merge(year_field_breakdown,
                              labels[c("general_field", "field_n_label")])

(plot_data_year_field <-  year_field_breakdown %>%
  filter(year != "2024")%>%
  select(-c(n, n_pubs, n_cits, n_att, overall_field_short))%>%
  group_by(year, field_n_label)%>%
  summarise(w = mean(w),
            w_att = mean(w_att),
            w_pubs = mean(w_pubs),
            w_cits = mean(w_cits))%>%
  pivot_longer(w:w_cits, names_to = "type", values_to = "share_women") %>%
    ggplot(aes(color=type, y=share_women, x=year, group = type)) + 
    geom_line()+
    facet_wrap(.~field_n_label, scales = "free")+
    scale_color_hue(labels = c("Professors", "In top 5% attention",
                                  "In top 5% citations", "In top 2% publication counts"))+
    labs(x = 'Year', y = "Share women", color = "")+
    theme_minimal())

```


# Individual paths

Get some insights into the paths of professors over time in terms of
their citations, publications, and media attention:


1. Top 30 people in total pub counts in our dataset:

```{r}
prof_year_p_c_g_a_t_l <-  prof_year_p_c_g_a_t_l %>%
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))



top_20_pubs <- prof_year_p_c_g_a_t_l %>%
  group_by(profile_id)%>%
  filter(year == max(year)) %>% 
  ungroup()%>%
  group_by(general_field)%>%
  slice_max(count_pubs_total, n = 30)


prof_year_p_c_g_a_t_l %>%
  filter(profile_id %in% top_20_pubs$profile_id & year < 2024 & !is.na(general_field))%>%
  ggplot(aes(x=years_since_first_pub, y=count_pubs_total, group=profile_id, color=profile_id)) +
  geom_line(aes(linetype=inferred_gender))+
  guides(color = FALSE)+
  facet_wrap(.~general_field, scales = "free_y")+
  theme_minimal()
  
```

2. Top 30 people in total citations in our dataset:

```{r}
top_20_cits <- prof_year_p_c_g_a_t_l %>%
  group_by(profile_id)%>%
  filter(year == max(year)) %>% 
  ungroup()%>%
  group_by(general_field)%>%
  slice_max(cited_by_total_all, n = 30)


prof_year_p_c_g_a_t_l %>%
  filter(profile_id %in% top_20_cits$profile_id & year < 2024 & !is.na(general_field))%>%
  ggplot(aes(x=years_since_first_pub, y=cited_by_total_all, group=profile_id, color=profile_id)) +
  geom_line(aes(linetype=inferred_gender))+
  guides(color = FALSE)+
  facet_wrap(.~general_field, scales = "free_y")+
  theme_minimal()
```

3. Top 30 people in total news attention in our dataset:

```{r}
top_20_news <- prof_year_p_c_g_a_t_l %>%
  group_by(profile_id)%>%
  filter(year == max(year)) %>% 
  ungroup()%>%
  group_by(general_field)%>%
  slice_max(attn_news_by_total, n = 30)


prof_year_p_c_g_a_t_l %>%
  filter(profile_id %in% top_20_news$profile_id & year < 2024 & !is.na(general_field))%>%
  ggplot(aes(x=years_since_first_pub, y=attn_news_by_total, group=profile_id, color=profile_id)) +
  geom_line(aes(linetype=inferred_gender))+
  guides(color = FALSE)+
  facet_wrap(.~general_field, scales = "free_y")+
  theme_minimal()
```

