---
title: "Untitled"
author: "Ana Macanovic"
date: "2024-02-29"
---

```{r}
options(width = 120)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
```


Load the packages:
```{r message=  F, warning = F, eval = T}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "tidyverse", "RPostgres", "lubridate", "psych",
                      "gridExtra",
                      "panelr", "skimr",
                      "lmtest", "sandwich")
groundhog.library(packages_to_load, date = "2023-12-01")

```

Load the panel:
```{r warning = F, message = F}
prof_year_p_c_g_a_t <-  read_csv("panel_datasets/prof_year_p_c_g_a_t.csv")
prof_year_p_c_g_a_t_l <-  read_csv("panel_datasets/prof_year_p_c_g_a_t_l.csv")
```
 
# Simple descriptives

Professors per field and subfield?
```{r}
print.data.frame(prof_year_p_c_g_a_t %>%
  distinct(profile_id, .keep_all = TRUE)%>%
  filter(!is.na(yearly_field))%>%
  group_by(yearly_field)%>%
  summarise(n = n())%>%
  arrange(-n))
```

```{r}
print.data.frame(prof_year_p_c_g_a_t %>%
  distinct(profile_id, .keep_all = TRUE)%>%
  filter(!is.na(yearly_subfield))%>%
  group_by(yearly_subfield)%>%
  summarise(n = n())%>%
  arrange(-n))
```

A correlation matrix:
```{r}
round(cor(prof_year_p_c_g_a_t[c("count_pubs", "cited_by",
                              "attn_news_by", "attn_blogs_by", "attn_twitter_by")],
          use="complete.obs"), 2)
```

And some descriptives:
```{r}
psych::describe(prof_year_p_c_g_a_t[c("count_pubs", "cited_by",
                             "attn_news_by", "attn_blogs_by",
                             "attn_twitter_by")])
```

Get some panel statistics:
```{r}
xtsum::xtsum(
  prof_year_p_c_g_a_t,
  variables = c("count_pubs", "cited_by",
                "attn_news_by", "attn_blogs_by", "attn_twitter_by"),
  id = "profile_id",
  t = "year",
  na.rm = TRUE,
  return.data.frame = FALSE,
  dec = 2
)
```

# Simple models

## Only gender

Publications and gender:
```{r}
gender_pubs <- lm(count_pubs~inferred_gender, 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_pubs, vcov = vcovCL(gender_pubs, cluster = ~profile_id))
```
Citations and gender:
```{r}
gender_cits <- lm(cited_by~inferred_gender, 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_cits, vcov = vcovCL(gender_cits, cluster = ~profile_id))
```

News attention and gender:
```{r}
gender_news <- lm(attn_news_by~inferred_gender, 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))
```
Blog attention and gender:
```{r}
gender_blogs <- lm(attn_blogs_by~inferred_gender, 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_blogs, vcov = vcovCL(gender_blogs, cluster = ~profile_id))
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(attn_twitter_by~inferred_gender, 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))
```

## Gender and fields:

Reference:  "Agricultural and Biological Sciences" 

Publications and gender:
```{r}
gender_pubs <- lm(count_pubs~inferred_gender+as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_pubs, vcov = vcovCL(gender_pubs, cluster = ~profile_id))
```
Citations and gender:
```{r}
gender_cits <- lm(cited_by~inferred_gender+as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_cits, vcov = vcovCL(gender_cits, cluster = ~profile_id))
```

News attention and gender:
```{r}
gender_news <- lm(attn_news_by~inferred_gender+as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))
```
Blog attention and gender:
```{r}
gender_blogs <- lm(attn_blogs_by~inferred_gender+as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_blogs, vcov = vcovCL(gender_blogs, cluster = ~profile_id))
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(attn_twitter_by~inferred_gender+as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))
```


## Gender and controls (not lagged)

News attention and gender:
```{r}
gender_news <- lm(attn_news_by~count_pubs + cited_by + inferred_gender + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Blog attention and gender:
```{r}
gender_blogs <- lm(attn_blogs_by~count_pubs + cited_by + inferred_gender + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_blogs, vcov = vcovCL(gender_blogs, cluster = ~profile_id))

summary(gender_blogs)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(attn_twitter_by~count_pubs + cited_by + inferred_gender + as.factor(overall_field),
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```



## Gender and controls (lagged)

News attention and gender:
```{r}
gender_news <- lm(attn_news_by~count_pubs_l + cited_by_l + inferred_gender + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Blog attention and gender:
```{r}
gender_blogs <- lm(attn_blogs_by~count_pubs_l + cited_by_l + inferred_gender + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_blogs, vcov = vcovCL(gender_blogs, cluster = ~profile_id))

summary(gender_blogs)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(attn_twitter_by~count_pubs_l + cited_by_l + inferred_gender + as.factor(overall_field),
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```

## Cumulative media attention?

Sure, seems there. 

News attention and gender:
```{r}
gender_news <- lm(attn_news_by~attn_news_by_l + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Blog attention and gender:
```{r}
gender_blogs <- lm(attn_blogs_by~attn_blogs_by_l + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_blogs, vcov = vcovCL(gender_blogs, cluster = ~profile_id))

summary(gender_blogs)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(attn_twitter_by~attn_twitter_by_l + as.factor(overall_field),
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```





## Cumulative media attention per gender?

Only for blogs?

News attention and gender:
```{r}
gender_news <- lm(attn_news_by~attn_news_by_l*inferred_gender + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Blog attention and gender:
```{r}
gender_blogs <- lm(attn_blogs_by~attn_blogs_by_l*inferred_gender + as.factor(overall_field), 
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_blogs, vcov = vcovCL(gender_blogs, cluster = ~profile_id))

summary(gender_blogs)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(attn_twitter_by~attn_twitter_by_l*inferred_gender + as.factor(overall_field) +years_since_first_pub*inferred_gender,
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```
NBA PAPER

```{r}
cor(prof_year_p_c_g_a_t_l[c("attn_twitter_by", "attn_twitter_by_total")],
          use="complete.obs")
```
DO THE VIF. 
```{r}
gender_twitter <- lm(attn_twitter_by~attn_twitter_by_l + count_pubs_l + cited_by_l   + inferred_gender + as.factor(overall_field) +years_since_first_pub,
                  data = prof_year_p_c_g_a_t_l)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```
the model above, watching out for totals etc. 
+ 
 
Network
- coauthors 
- coauthors cites
- coauthors attention
- are these for t or t-1

Share of coauthors in the high end of attention distribution.


- any attention (are you in the attention elite)
- amount of attention
- top 10%

PUB TYPE
- articles, books + book chapters
- preprints? conf. proceedings?
