---
title: "Dutch media profs scripts"
output:
  html_document:
    toc: false
    number_sections: false
author: "by: Ana Macanovic and Bas Hofstra"
bibliography: references.bib

---


```{r, install remotely, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
# install.packages("remotes")
#remotes::install_github("rlesur/klippy")
``` 

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


----

:::::::::::::: {.columns}
::: {.column width="80%"}

# Repository Description
Last compiled on `r format(Sys.time(), '%B %d, %Y')`  

This website shows the script for the Dutch Media Profs project.
This project explores gender inequalities in media representation between men and women 
professors in the Netherlands.

The project is conducted by [Bas Hofstra](https://www.bashofstra.com) and [Ana Macanovic](https://amacanovic.github.io/)
at the [Radboud University](https://www.ru.nl/en).

This project answers these questions by considering whether and why women professors 
are represented in news and social media at different numbers than men professors. 
This representation in the public arena has become increasingly important for 
professors as the dissemination of scientific knowledge to the general public is 
a growing and essential part of professors’ activities and evaluation. This project
sets out to study this among all Dutch professors (1990-2021) through a series of 
new database linkages and computational methods.

We start with a dataset of 6830 professors as per NARCIS (National Academic Research
and Collaboration Information System), a former Dutch nationala information portal
for Dutch scientific data and publications. 

For each professor, we collect the following data:

- Publication, citation, affiliation, topic, concept, and grant data from [OpenAlex](https://openalex.org/)
- Printed news articles containing a professors first and last names and a set of
keyword related to their academic roles from [LexisNexis](https://www.lexisnexis.com/).
- Online news mentions and number of Tweets pertaining to their publications from [Altmetric](https://www.altmetric.com/)
- Dutch grant data from [NWO](https://www.nwo.nl/) and ERC grant data from the [ERC datahub](https://erc.easme-web.eu?mode=7&countries=NL):


<br>

Before beginning, make sure you install the groundhog package:
```{r eval = FALSE}
install.packages("groundhog")
```


----


:::
::: {.column width="80%"}


:::
::::::::::::::



## Contents

<br>

Use the top menu to navigate through the currently finished scripts, including:

- An introduction to accessing our database using SQL
- Prep. 1: A script including Open Alex and Altmetric data download
- Prep. 2: A script for gender inference
- Prep. 3: A script parsing grant data retrieved from the NWO
- Prep. 4: A script parsing data retrieved from LexisNexis (no access to LexisNexis retrieval code is available)
- Prep. 5: Compilation of a panel dataset following professor's careers over years
- Main analyses
- Suppl. 1: Descriptives on our database and comparison of publication coverage between OpenAlex and NARCIS publication data
- Suppl. 2: Data descriptives presented in the first subsection of the Online Supplement
- Suppl. 3: Additional analyses and regression robustness checks
- Suppl. 4: Additional functions used in other scripts

----






