---
title: "Untitled"
author: "Ana Macanovic"
date: "2024-03-06"
output: html_document
---
Mentions and journalist gender.

```{r}
knitr::opts_chunk$set(eval = FALSE)
```

Load the packages:
```{r message=  F, warning = F}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", "stringr",
                      "tidyverse", "RPostgres", "lubridate",
                      "digest", "DBI", "RODBC", "odbc")
groundhog.library(packages_to_load, date = "2023-12-01")
```

Connect to the database:
```{r}
port <- 
user <- ""
password <- ""
database_name <- ""

con <- RPostgres::dbConnect(RPostgres::Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)
```

Load the mentions, author names/genders, and the link between professors and mentions:
```{r}
pub_news <- dbReadTable(con, "altmetric_pub_att_news")

news_mentions_full <- dbReadTable(con, "pub_att_news_full_text")

news_authors <- dbReadTable(con, "pub_att_news_author_names_gender")
```

Merge publications with author details:
```{r}
pub_news_authors <- merge(pub_news,
                          news_authors,
                          all.x = TRUE,
                          by = "url")

pub_news_authors$gender <- ifelse(pub_news_authors$gender == "female",
                                  "w",
                                  ifelse(pub_news_authors$gender == "male",
                                         "m", pub_news_authors$gender))

pub_news_authors$gender <- ifelse(is.na(pub_news_authors$gender),
                                  "missing",
                                  pub_news_authors$gender)

pub_news_authors$full_text <- ifelse(pub_news_authors$url %in% news_mentions_full$url,
                                     "true",
                                     "false")

```

For those where we have the gender, merge with the professors and check:
```{r}
pub_news_w_gender <- filter(pub_news_authors, gender != "missing")

oa_prof_pub_match <- dbReadTable(con, "oa_prof_pub_match")

pub_news_w_gender <- merge(pub_news_w_gender,
                           oa_prof_pub_match,
                           by = "id")
```

And match with prof gender:
```{r}
prof_gender <- dbReadTable(con, "gender_table")

pub_news_w_prof_gender <- merge(pub_news_w_gender,
                                prof_gender[c("profile_id", "inferred_gender")],
                                by = "profile_id")
```

Reporters:
```{r}
table(pub_news_w_gender$gender)
prop.table(table(pub_news_w_gender$gender))
```

Men reporters write about:
```{r}
men_pub_news <- filter(pub_news_w_prof_gender, gender == "m")

prop.table(table(men_pub_news$inferred_gender))*100

women_pub_news <- filter(pub_news_w_prof_gender, gender == "w")

prop.table(table(women_pub_news$inferred_gender))*100
```

Connect to the field:
```{r}
prof_year_p_c_g_a_t <- read_csv("prof_year_p_c_g_a_t_l.csv")

prof_fields <- prof_year_p_c_g_a_t %>%
  distinct(profile_id, .keep_all = TRUE)%>%
  select(profile_id, overall_field, inferred_gender)

prof_fields_genders <- prof_fields %>%
  group_by(overall_field)%>%
  summarise(researchers = n(),
            women = sum(inferred_gender == "w"),
            men = sum(inferred_gender == "m"))

prof_fields_genders$perc_women <- round((prof_fields_genders$women/prof_fields_genders$researchers)*100,2)
```

Get the field and the gender of the mentioned professor:
```{r}
pub_news_authors_prof <- merge(pub_news_authors, 
                               oa_prof_pub_match,
                               by = "id")
```




```{r}
pub_news_w_prof_gender_field <- merge(pub_news_w_prof_gender,
                                      prof_fields,
                                      by = "profile_id")

fields_journalists <- pub_news_w_prof_gender_field %>%
  group_by(overall_field)%>%
  summarise(articles = n(),
            women_journalists = sum(gender == "w"),
            men_journalists = sum(gender == "m"),
            about_women = sum(inferred_gender == "w"),
            about_men = sum(inferred_gender == "m"),
            w_abt_w = sum(gender == "w" & inferred_gender == "w"),
            w_abt_m = sum(gender == "w" & inferred_gender == "m"),
            m_abt_w = sum(gender == "m" & inferred_gender == "w"),
            m_abt_m = sum(gender == "m" & inferred_gender == "m"))

fields_journalists$perc_about_women <- round(fields_journalists$about_women/fields_journalists$articles*100, 2)

```



fields_journalists <- fields_journalists %>%
  pivot_wider(names_from = gender, values_from = n)

fields_journalists$share_women_authored <- round(fields_journalists$w / (fields_journalists$m + fields_journalists$w)*100)

fields_journalists <- fields_journalists %>% select(overall_field, share_women_authored)
```

