---
title: "OpenAlex_Altmetric_data_download"
author: "Ana Macanovic"
date: "2023-12-06"
---


This script uses OpenAlex database to download data on the professors in our sample

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

Load the packages:
```{r message=  F, warning = F}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "openalexR",
                      "ggplot2", "stringr", "tidyr",
                      "jsonlite")
groundhog.library(packages_to_load, date = "2023-12-01")

# we've also added our email to the "polite pool" of OpenAlex by
# adding a line in the .Rprofile
```

# Tidy up professor data from NARCIS

Load the professor profiles:
```{r message = F, warning = F}
load("raw_data/media_profs_profiles.rda")
profs <- read_csv("raw_data/dutch_profs_urls.csv")

# merge the profs with their ORCIDs
colnames(profs)[c(1,7)] <- c("id", "profile_id")

profs_full <- merge(profs,
                    metadf[, c(1:4, 361)],
                    by = "profile_id")
```

# Tidy up the publication data from NARCIS
Load the publication data:
```{r}
# fetch the papers
load("~/Postdoc/Projects/dutch_media_profs_r/raw_data/media_profs_pubs.rda")
# match the publication data to authorships
load("~/Postdoc/Projects/dutch_media_profs_r/raw_data/media_profs_pub_to_profile_ids.rda")
colnames(pub_to_profile_id)[1] <- "narcis_url"

prof_pubs_full <- merge(pubs_metadf[, c(1:23)],
                        pub_to_profile_id,
                        by = "narcis_url")
# strip the last / from the profile ids here
prof_pubs_full$profile_id <- str_sub(prof_pubs_full$profile_id, end = -2)

# tidy up some misbehaving DOIs
prof_pubs_full$n_words <- str_count(prof_pubs_full$DOI, " ")

# let's manually fix them since there are so few problematic ones
pubs_doi_words <- filter(prof_pubs_full, n_words > 0)
# these are just the DOIs where we have manually removed the spaces or redundant text
pubs_doi_words$DOI <- c("10.1016/j.jhydrol.2011.03.047", "10.1111/j.1365-3091.2012.01365.x",   
                         "10.1120/jacmp.v17i4.6117", "10.22203/ecm.v032a11",  
                         "10.22203/ecm.v032a11", "10.1167/iovs.16-20799",  
                         "10.1136/bmjsem-2018-000427", "10.1111/hae.12353",
                         "10.1128/iai.64.10.4220-4225.1996", "10.1039/b302097e",       
                         "10.1039/b302097e", "10.1016/s0016-5085(19)38052-7",
                         "10.1039/b209378b", "10.3850/978-981-07-2615-7-290",      
                         "10.3850/978-981-07-2615-7 289", "10.1016/s0040-6090(96)09248-6",    
                         "10.1061(asce)mt.1943-5533.0002169", "10.1371/journal.pone.0059600",     
                         "10.1371/journal.pone.0059600", "10.1371/journal.pone.0059600",     
                         "10.1109/isbi.2016.7493532", "10.1109/isbi.2016.7493532",         
                         "10.1109/isbi.2016.7493532", "10.1109/isbi.2016.7493532",         
                         "10.1109/isbi.2016.7493532", "10.1080/03797720120082651",         
                         "10.3850/978-981-11-2724-3_0641-cd", "10.3850/978-981-11-2724-3_0641-cd", 
                         "10.3850/978-981-11-2724-3_0596-cd", "10.1136/bmjopen-2017-016077",       
                         "10.1103/physrevlett.115.159901", "10.1515/lingvan-2016-0048",         
                         "10.1108/jfrc-07-2018-0103", "10.1097/01.brs.0000206381.15224.0",
                         "10.1080/21507740.2016.1251990", "10.1021/ie0492449 s0888-5885(04)09244-9",  
                         "10.1021/ie0492449 s0888-5885(04)09244-9", "10.2478/v10304-012-0011-y",   
                         "10.1007/s10853-011-5682-6", "10.1021/ja0455650s0002-7863(04)05565-9",   
                         "10.1021/jo0401220-s0022-3263(04)00122-7","10.1007/s10103-008-0626-3",  
                         "10.1371/journal.pone.0216743", "10.1177/0021886316672724",         
                         "10.5194/se-10-517-2019", "10.18690/978-961-286-061-5.3",      
                         "10.18690/978-961-286-061-5.3", "10.3850/978-981-11-2724-3_0441-cd", 
                         "10.3850/978-981-11-2725-0-is3-5-cd", "10.3390/atmos12121633",  
                         "10.3850/978-981-14-8593-0-4139-cd", "10.3850/978-981-11-2724-3_0248-cd") 
# fix the pub list
# filter out the problematic dois
prof_pubs_full_fix <- filter(prof_pubs_full, (is.na(n_words)|n_words == 0))
# and then put them back
prof_pubs_full <- rbind(prof_pubs_full_fix,
                        pubs_doi_words)


# drop large files from the memory as we don't need them anymore
rm(pubs_metadf)
rm(metadf)
rm(pub_to_profile_id)
rm(narcis_ids)
gc()
```


# Define the data querying function

First, define a helper function that will query the Altmetric API using pub DOIs:
```{r}
altmetric_mention_retriever <- function(api_key,
                                        publication_list,
                                        include_twitter = FALSE){
  
  # elements to make a url that calls the API to get mention data
  doi_call_url <- "https://api.altmetric.com/v1/fetch/doi/"
  api_key_url <- paste0("?key=", api_key)
  exclude_twitter_url <- "&exclude_sources=twitter"
  
  # get the publication list
  oa_pubs <- publication_list
  # if not empty:
  if (!is.null(nrow(oa_pubs))){
    # loop, for each doi, and:
    for (i in 1:nrow(oa_pubs)){
      # get the doi without the url part
      doi_url <- str_remove(oa_pubs$doi[i], "https://doi.org/")
      # if there is a doi:
      if (!is.na(doi_url)){
        # make the url for the api call
        api_call <- paste(doi_call_url, doi_url, api_key_url, sep = "")
        
        # exclude twitter? if so, add:
        if (include_twitter == FALSE){
          api_call <- paste(api_call, exclude_twitter_url, sep = "")
        }
        # empty DOI output object, in case try fails
        doi_output <- NA
        # and call the api
        try(doi_output <- fromJSON(txt=api_call), silent = TRUE)
        # now, check if this doi has any mentions in the media
        if ("posts" %in% names(doi_output)){
          mentions <- doi_output[["posts"]]
          # since different papers have different mentions, let's loop again
          # addding columns for relevant mentions
          for (mention_type in names(mentions)){
            # check if column already there in oa_pubs
            if(mention_type %in% colnames(oa_pubs)){
              # if there, just add the mentions into the cell (nested)
              oa_pubs[[which(colnames(oa_pubs)==mention_type)]][i] <- list(mentions[[mention_type]])
            }else{
              # if column not there, first add it and populate with NAs
              oa_pubs[mention_type] <- NA
              # and then, for this pub, paste the mention data into the cell (it will be a nested dataframe)
              oa_pubs[[which(colnames(oa_pubs)==mention_type)]][i] <- list(mentions[[mention_type]])
            }
          }
        }
      }
    }
  }
  # return the list of publications dataframe with new columns
  return(oa_pubs)
}
```




Define a function that will query Open Alex and Altmetric APIs at once, collecting 
various information abut each professor from their Narcis ID:
```{r}
professor_info_retriever <- function(narcis_id,
                                     pub_data,
                                     prof_data,
                                     api_key,
                                     # recommend to set to FALSE unless all works well,
                                     # to avoid using up our twitter query limits
                                     include_twitter = FALSE){
  
  # get the professor's narcis id anad get their publications based on this
  prof_pubs <- filter(pub_data, profile_id == narcis_id)
  # get their name
  prof_name_details <- filter(prof_data, profile_id == narcis_id)
  prof_name <- paste(prof_name_details$first, 
                     prof_name_details$last)
  
  # get their initials, drop their name in the brackets
  prof_initials <- str_squish(str_split_i(prof_name_details$initialen, "\\(", 1))
  # but some profs might have a roepnaam which is not the name they use
  # to sign their papers (the brackets will contain the roepnaam, but the
  # initials will be containing the actual first name)
  # get an additional option w/o the first name at all
  prof_initials_wo_first_name <- paste(str_split(prof_initials, "\\.")[[1]], collapse = ".")
  # and space them out
  prof_initials_wo_first_name_space <- paste(str_split(prof_initials, "\\.")[[1]], collapse = ". ")
  
  prof_initials <- str_split(prof_initials, "\\.")[[1]][-c(1, length(str_split(prof_initials, "\\.")[[1]]))]
  prof_initials_no_space <- paste0(paste(prof_initials, collapse = "."), ".")
  prof_initials_space <- paste0(paste(prof_initials, collapse = ". "), ".")
  # professor first name, initials, last name
  prof_name_w_initials <-  tolower(paste(paste(prof_name_details$first, 
                                               prof_initials_no_space),
                                         prof_name_details$last))
  # professor first name, initials, last name, with spaces between the initials
  prof_name_w_initials_space <-  tolower(paste(paste(prof_name_details$first, 
                                                     prof_initials_space),
                                               prof_name_details$last))
  
  # just the first letter of the name + initials
  # with spacing
  first_initials_space <- paste(paste0(substring(prof_name_details$first, 1, 1), "."),
                                prof_initials_space)
  
  prof_name_first_initials_space <- tolower(paste(first_initials_space, 
                                                  prof_name_details$last))
  # w/o spacing
  first_initials <- str_remove_all(paste(paste0(substring(prof_name_details$first, 1, 1), 
                                                "."),
                                         prof_initials_space), " ")
  
  prof_name_first_initials <- tolower(paste(first_initials, 
                                            prof_name_details$last))
  
  # for some professors, we manually find their actual name vs their roepnaam in NARCIS
  prof_alternative_full_name <- ""
  if (narcis_id == "https://www.narcis.nl/person/RecordID/PRS1239190"){
  prof_alternative_full_name <- tolower("Albert M. Brouwer")
  }
  
  # get the DOI list without the NAs
  doi_list <- prof_pubs$DOI[!is.na(prof_pubs$DOI)]
  # if any DOIs in our list:
  if (length(doi_list)>0){
    # call OpenAlex to get their works based on the DOIs
    # do it in batches (currently 25)
    batch_size <- 25
    batches <- ceiling(length(doi_list)/batch_size)
    prof_works_oa <- data.frame(matrix(NA, ncol = 16, nrow = 0))
    begin_batch <- 1
    end_batch <- batch_size
    # initialize an empty data frame
    prof_works_oa_batch <- data.frame(matrix(NA, ncol = 16, nrow = 0))
    # loop through the batches
    for(i in 1:batches){
      # get the first batch
      # try, if error, just stop
      try(
        prof_works_oa_batch <- oa_fetch(
          entity = "works",
          doi = doi_list[begin_batch:end_batch]), 
        silent = TRUE
      )
      # when binding, some columns might not be there
      # so to address that, check the columns
      # if the new batch has less (but only after the first batch was processed, thus i > 1)
      if (i > 1 & length(which(!colnames(prof_works_oa) %in% colnames(prof_works_oa_batch))) > 0){
        # add the missing columns filled with NAs
        prof_works_oa_batch[colnames(prof_works_oa)[which(! colnames(prof_works_oa) %in% colnames(prof_works_oa_batch))]] <- NA
        # rearrange the columns
        prof_works_oa_batch <- prof_works_oa_batch[colnames(prof_works_oa)]
      }
      # if the new batch has more (but only after the first batch was processed, thus i > 1)
      if (i > 1 & length(which(! colnames(prof_works_oa_batch) %in% colnames(prof_works_oa))) > 0){
        # add the missing columns filled with NAs
        prof_works_oa[colnames(prof_works_oa_batch)[which(! colnames(prof_works_oa_batch) %in% colnames(prof_works_oa))]] <- NA
        # rearrange the columns
        prof_works_oa <- prof_works_oa[colnames(prof_works_oa_batch)]
      }
      
      # bind to the rest
      prof_works_oa <- rbind(prof_works_oa,
                             prof_works_oa_batch)
      
      # get the remaining batch size, and go to the end if less than batch size, 
      # and go for another round if more than batch size
      if (length(doi_list)-end_batch <= batch_size){
        end_batch <- end_batch + length(doi_list)-end_batch
      }else{
        end_batch <- end_batch + batch_size
      }
      # set the beginning to the beginning + batch size
      begin_batch <- begin_batch + batch_size
    }
    
    # and now loop through the authors of these papers in OpenAlex to get info
    # on the author ids OpenAlex has on them
    prof_oaid_info <- data.frame(matrix(NA, nrow = 0, ncol = 13))
    # loop through the papers we retrieved, get the DOIs and author lists and try to match the
    # author to those we miss
    if (nrow(prof_works_oa) > 0){
      for (i in 1:nrow(prof_works_oa)){
      author_info <- c()
      info <- prof_works_oa[i, c("id","display_name", "doi")]
      doi_in_question <- str_remove(info$doi, "https://doi.org/")
      # if found and one person
      authors <- prof_works_oa[i, "author"][[1]][[1]]
      if (class(authors) != "logical"){
        # find the author with a matching name
        authors$match <- grepl(prof_name, tolower(authors$au_display_name))
        # check with initials as well
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_name_w_initials, tolower(authors$au_display_name)),
                                authors$match)
        # and spaced out initials
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_name_w_initials_space, tolower(authors$au_display_name)),
                                authors$match)
        # and no first name, but only initials and also only spaced out initials
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_name_first_initials, tolower(authors$au_display_name)),
                                authors$match)
        
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_name_first_initials_space, tolower(authors$au_display_name)),
                                authors$match)
        
        # if nothing still, initials without the first name
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_initials_wo_first_name, tolower(authors$au_display_name)),
                                authors$match)
        
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_initials_wo_first_name_space, tolower(authors$au_display_name)),
                                authors$match)   
        # and their alternative first name we manually correct for
        authors$match <- ifelse(authors$match == FALSE,
                                grepl(prof_alternative_full_name, tolower(authors$au_display_name)),
                                authors$match)   
        
        # fetch the author, if there is a match
        author <- filter(authors, match == TRUE)
        
        if (nrow(author) == 1){
          # remove the "match" column
          author_info <- author[, -12]
          # bind with the narcis ID for later
          author_info$profile_id <- narcis_id
        }
      }
      
      prof_oaid_info <- rbind(prof_oaid_info,
                              author_info)
    }
    
    # get all oa ids of the author
    oa_ids <- as.character(unique(prof_oaid_info$au_id))
    }
    
    # if ID found:
    if (length(oa_ids)>0){
      # get all papers from OA using these ids:
      prof_all_works_oa <- oa_fetch(
        entity = "works", 
        author.id = oa_ids)
      
            
      # now, merge the works based on the doi and those based on the OA ID
      prof_all_works_oa <- rbind(prof_works_oa,
                                 prof_all_works_oa)
      prof_all_works_oa$duplicate <- duplicated(prof_all_works_oa[, c("id")])
      # deduplicate
      prof_all_works_oa <- filter(prof_all_works_oa,
                                  duplicate == FALSE)
      
      # if there are still duplicates, deduplicate by lowercased title
      prof_all_works_oa$display_name_lower <- tolower(prof_all_works_oa$display_name)
      prof_all_works_oa$duplicate <- duplicated(prof_all_works_oa[, c("display_name_lower")])
      prof_all_works_oa <- filter(prof_all_works_oa,
                                  duplicate == FALSE)
      
      # paste the OA ID and the Narcis ID
      prof_all_works_oa$oa_id <- paste(oa_ids, collapse = ", ")
      prof_all_works_oa$profile_id <- narcis_id
      
      # get their co-authors in a given year
      # but also their affiliations, and the autoship positino in every pub, 
      # since we are already looping...
      # pleceholder for authoship position
      prof_pub_position <- rep(NA, nrow(prof_all_works_oa))
      # placeholders for authors and affiliations
      prof_coauthors_oa <- NA
      prof_pub_info_ia <- NA
      
      for (i in 1:nrow(prof_all_works_oa)){
        # fetch the authors nested within the "author" field returned by OA
        all_authors <- prof_all_works_oa[i, "author"][[1]][[1]]
        # get the professor info and their affiliations that year
        prof_author_info <- filter(all_authors,  au_id %in% oa_ids)
        # if author's ID not found here (e.g., a slightly different name), it will be set to NA
        prof_pub_position[i] <- NA
        # otherwise, replace with the actual value
        if (nrow(prof_author_info)>0){
        # paste the prof's authorship here
        prof_pub_position[i] <- prof_author_info[, 'author_position']
        }
        # exclude this author themselves from the co-authors
        coauthors <- filter(all_authors, ! au_id %in% oa_ids)
        # if not a single-author paper, get coauthor info
        if (nrow(coauthors) > 0){
          # get the publication year
          year <- as.numeric(prof_all_works_oa[i, "publication_year"])
          # paste the year alongside the coauthors
          coauthors$year <- year
          prof_coauthors_oa <- rbind(prof_coauthors_oa,
                                     coauthors)
        }
        # for the prof themselves, get their affiliation info etc
        if (nrow(prof_author_info) > 0){
          # get the publication year
          year <- as.numeric(prof_all_works_oa[i, "publication_year"])
          # paste the year alongside the coauthors
          prof_author_info$year <- year
          prof_pub_info_ia <- rbind(prof_pub_info_ia,
                                    prof_author_info)
        }
      }
      # tidy up the dataframe on coauthors, if any info is there
      if (!is.null(nrow(prof_coauthors_oa))){
        if (nrow(prof_coauthors_oa) > 0){
          
          # and deduplicate coauthorships in the same year
          prof_coauthors_oa$duplicate <- duplicated(prof_coauthors_oa[, c("au_id", "year")])
          prof_coauthors_oa <- filter(prof_coauthors_oa,
                                      duplicate == FALSE)
          # remove the duplicate column
          prof_coauthors_oa <- prof_coauthors_oa[, -ncol(prof_coauthors_oa)]
          
          # remove the row with NAs
          prof_coauthors_oa <- prof_coauthors_oa[rowSums(is.na(prof_coauthors_oa)) != ncol(prof_coauthors_oa), ]
          
          # add the author id info just in case
          prof_coauthors_oa$oa_id <- paste(oa_ids, collapse = ", ")
          prof_coauthors_oa$profile_id <- narcis_id
        }
      }
      
      # tidy up the info on author affiliations, if any is there
      if (!is.null(nrow(prof_pub_info_ia))){
        # once again, if any is there...
        if (nrow(prof_pub_info_ia) > 0 ){
          prof_pub_info_ia <- filter(prof_pub_info_ia, !is.na(institution_id))
          # check that filtering did not remove everything; if so, replace back with NA
          if (nrow(prof_pub_info_ia) == 0){
            prof_pub_info_ia <- NA
          }else{
            # and deduplicate affiliations in the same year
            prof_pub_info_ia$duplicate <- duplicated(prof_pub_info_ia[, c("institution_id", "year")])
            prof_pub_info_ia <- filter(prof_pub_info_ia,
                                       duplicate == FALSE)
            # remove the duplicate column
            prof_pub_info_ia <- prof_pub_info_ia[, -ncol(prof_pub_info_ia)]
            
            # drop author position since this is paper related
            prof_pub_info_ia <- prof_pub_info_ia[ , -which(names(prof_pub_info_ia) %in% c("author_position"))]
            # add the author id info just in case
            prof_pub_info_ia$oa_id <- paste(oa_ids, collapse = ", ")
            prof_pub_info_ia$profile_id <- narcis_id
          }
        }
      }
      
      # add the authorship info to the publications
      prof_all_works_oa$author_position <- prof_pub_position
      
      # initialize an empty object for grant info
      prof_grants_oa <- NA
      
      # if there is a grant column, fetch their grant numbers
      if ("grants" %in% colnames(prof_all_works_oa)){
        # get the grant list
        prof_grant_list <- prof_all_works_oa$grants
        # get the years from the publications
        year_list <- prof_all_works_oa$publication_year
        # empty dataframe
        #prof_grants_oa <- data.frame(matrix(NA, nrow = 0, ncol = 5))
        # for each grant item in the list
        for (i in 1:length(prof_grant_list)){
          grant <- prof_grant_list[[i]]
          # if not NA, get the data
          if (! anyNA(grant)){
            # get all funder IDs and names and put them into a dataframe
            # NB: not all of these are author's own grants, but they are
            # co-authorship grants
            funder_ids <- grant[names(grant)=="funder"]
            funder_names <- grant[names(grant) == "funder_display_name"]
            year <- as.numeric(year_list[i])
            oa_id <- paste(oa_ids, collapse = ", ")
            profile_id <- narcis_id
            fund_df <- cbind.data.frame(funder_id = funder_ids,
                                        funder_names = funder_names)
            # add some more info
            fund_df$year <- year
            fund_df$oa_id <- paste(oa_ids, collapse = ", ")
            fund_df$profile_id <- narcis_id
            prof_grants_oa <- rbind(prof_grants_oa,
                                    fund_df)
          }
        }
        # if not NA, tidy up the dataframe
        if (!is.null(nrow(prof_grants_oa))){
          # tidy up the row names
          rownames(prof_grants_oa) <- 1:nrow(prof_grants_oa)
          # deduplicate same grants across years
          prof_grants_oa$duplicate <- duplicated(prof_grants_oa[, c("funder_id", "year")])
          prof_grants_oa <- filter(prof_grants_oa,
                                   duplicate == FALSE)
          # remove the duplicate column
          prof_grants_oa <- prof_grants_oa[, -(ncol(prof_grants_oa))]
          # remove the row with NAs
          prof_grants_oa <- prof_grants_oa[rowSums(is.na(prof_grants_oa)) != ncol(prof_grants_oa), ]
        }
      }
      
      # get the info on this author
      prof_info <- oa_fetch(
        entity = "authors", 
        identifier = oa_ids)
      
      # now, query the Altmetric API to get mentions info on the author
      prof_all_works_oa_mentions <- altmetric_mention_retriever(api_key = api_key,
                                                                publication_list = prof_all_works_oa,
                                                                include_twitter = include_twitter)
      
      
      # output a list populated with all the details
      prof_output <- list()
      prof_output["profile_id"] <- narcis_id
      prof_output["oa_ids"] <- list(oa_ids)
      prof_output["orcid"] <- prof_info$orcid
      prof_output["prof_info"] <- list(prof_info)
      prof_output["narcis_pubs"] <- list(prof_pubs)
      prof_output["oa_pubs"] <- list(prof_all_works_oa_mentions)
      prof_output["grant_info"] <- list(prof_grants_oa)
      prof_output["coauthor_info"] <- list(prof_coauthors_oa)
      prof_output["affiliation_info"] <- list(prof_pub_info_ia)
    }else{
      prof_output <- list()
      prof_output["profile_id"] <- narcis_id
      prof_output["oa_ids"] <- list(NA)
      prof_output["orcid"] <- prof_name_details$ORCID
      prof_output["prof_info"] <- list(NA)
      prof_output["narcis_pubs"] <- list(prof_pubs)
      prof_output["oa_pubs"] <- list(NA)
      prof_output["grant_info"] <- list(NA)
      prof_output["coauthor_info"] <- list(NA)
      prof_output["affiliation_info"] <- list(NA)
    }
    
  }else{
    # if no DOIs in our list, paste only the professor publications we have in NARCIS
    prof_output <- list()
    prof_output["profile_id"] <- narcis_id
    prof_output["oa_ids"] <- list(NA)
    prof_output["orcid"] <- prof_name_details$ORCID
    prof_output["prof_info"] <- list(NA)
    prof_output["narcis_pubs"] <- list(prof_pubs)
    prof_output["oa_pubs"] <- list(NA)
    prof_output["grant_info"] <- list(NA)
    prof_output["coauthor_info"] <- list(NA)
    prof_output["affiliation_info"] <- list(NA)
  }
  
  return(prof_output)
}
```



# Get the data

Fetch the data for the professors in our data:
```{r warning = F}
# api key (fill in own)
altmetric_api_key <- ''

# query in batches
narcis_ids <- profs_full$profile_id
# batch size
prof_batch_size <- 500
# vector of indices to loop through
batches <- seq(from=1, to=length(narcis_ids), by=prof_batch_size)
# to be able to subset, also add the final index+1
batches <- c(batches, length(narcis_ids)+1)

# loop through the batches

for(i in 1:(length(batches)-1)){
  # initialize an empty list for the batch
  batch_prof_outcomes <- list()
  # initialize a list for empty ouputs - profs that threw an error
  batch_errors <- list()
  
  # get the narcis ids from the batch
  prof_batch <- narcis_ids[batches[i]:(batches[i+1]-1)]
  
  # loop through professors in this batch
  for (narcis_id in prof_batch){
    # set outcome to NA as a placeholder
    outcome <- NA
    
    # try to query all the data
    try(outcome <- professor_info_retriever(narcis_id,
                                            pub_data = prof_pubs_full,
                                            prof_data = profs_full,
                                            api_key = altmetric_api_key,
                                            # recommend to set to FALSE unless all works well,
                                            # to avoid using up our twitter query limits
                                            include_twitter = FALSE), silent = TRUE)
    
    # append to the batch data
    batch_prof_outcomes[[narcis_id]] <- outcome
    if (is.na(outcome)){
    # if empty outcome, append to the error list
    batch_errors[[narcis_id]] <- outcome
    }
    # print some info out
    print(paste("done with", which(narcis_id == prof_batch), "out of", length(prof_batch)))
  }
  
  # save the batch RDS
  save_string <- paste0("processed_data/open_alex_prof_data/", paste("prof_data_batch", i, sep = "_"), ".RDS")
  saveRDS(batch_prof_outcomes, save_string)
  # and the error RDS
  save_string <- paste0("processed_data/open_alex_prof_data/", paste("prof_data_errors", i, sep = "_"), ".RDS")
  saveRDS(batch_errors, save_string)
}
```

The resulting output is a list of professors which contains, for each prof:

1. Author's NARCIS ID
2. Author's OA IDS (if found)
3. Author's ORCID (if found in either our data or OA)
4. Author info from IA
5. Author's publications as per the NARCIS record
6. Author's publications as per the OA record + nested mentions from the Altmetric API
7. Info on grants of author and their co-authors per year, extracted from publications in OA
8. Info on author's co-authors and co-author affiliations per year, extracted from publications in OA
9. Info on author's own affiliations per year, extracted from publications in OA



