---
title: "Professor-level descriptives"
author: "Ana Macanovic"
date: "2024-02-19"
---

Get an overview of our dataset at the professor level.

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE, cache.lazy = FALSE)
```

Loding the packages, and connecting to the database first. 
```{r message=  F, warning = F}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", "ggpubr",
                      "ggplot2", "knitr",
                      "tidyverse", "RPostgres", "lubridate",
                      "digest", "DBI", "RODBC", "odbc")
groundhog.library(packages_to_load, date = "2023-12-01")

# load the helper function file
source("helper_functions.R")

# fill in own credentials
port <- 5432
user <- "postgres"
password <- "dutchmediaprofssql"
database_name <- "postgres"

con <- RPostgres::dbConnect(RPostgres::Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)

con # Checks connection is working
```

# Data preparation

Loading professor profiles.
```{r message = F, warning = F}
narcis_prof_info <- dbReadTable(con, "narcis_prof_info")
```

Then, loading all the publications of professors from "oa_prof_pubs", getting 
unique publications, and getting professor totals.
```{r}
oa_pubs <- dbReadTable(con, "oa_prof_pubs")

oa_distinct_pubs <- oa_pubs%>%
  distinct(., id, .keep_all = TRUE)%>%
    select(-counts_by_year_year, -counts_by_year_cited_by_count)

profs_pubs_citations <- oa_distinct_pubs %>%
  group_by(profile_id)%>%
  summarise(
    pubs_total = n(),
    cited_by_total = sum(cited_by_count)
  )
```

Retrieving professors' coauthors from "oa_coauthor_info", getting their unique
coauthors (at least coauthored once), and getting a total.
```{r}
oa_coauthors <- dbReadTable(con, "oa_coauthor_info")

profs_coauthors <- oa_coauthors %>%
  distinct(., au_id, profile_id, .keep_all = TRUE)%>%
  group_by(profile_id)%>%
  summarise(
    coauthors_total = n())
```

Finally, get professor news media attention from "altmetric_pub_att_news" table,
and get the totals.
```{r}
altmetric_pub_att_news <- dbReadTable(con, "altmetric_pub_att_news")

altmetric_pub_att_news <- merge(altmetric_pub_att_news,
                                oa_distinct_pubs, 
                                by = "id",
                                all.x = TRUE)

profs_attention <- altmetric_pub_att_news %>%
  group_by(profile_id)%>%
  summarise(
    attention_total = n())
  
```

Combine these datasets and merge with professors' inferred gender table ("gender_table"),
```{r}
prof_table <- merge(profs_pubs_citations,
                    profs_coauthors,
                    by = "profile_id",
                    all.x = TRUE,
                    all.y = TRUE)

prof_table <- merge(prof_table,
                    profs_attention,
                    by = "profile_id",
                    all.x = TRUE,
                    all.y = TRUE)

gender_inference_table <- dbReadTable(con, "gender_table")

prof_table <- merge(prof_table,
                    gender_inference_table[c("profile_id", "inferred_gender")],
                    by = "profile_id",
                    all.x = TRUE,
                    all.y = TRUE)


prof_table <- prof_table %>%
  replace(is.na(.), 0)
```

Get some group means to plot mean lines in our histograms, and get separate
dataframes for men and women for mean testing.
```{r}
# get some means for lines in our histograms
means_prof_table <- prof_table %>%
  group_by(inferred_gender)%>%
  summarise(mean_pubs = mean(pubs_total),
            mean_coauthors = mean(coauthors_total),
            mean_attention = mean(attention_total))

men_profs <- filter(prof_table, inferred_gender == "m")
women_profs <- filter(prof_table, inferred_gender == "w")
```

Get, for each professor, the year of first publication in our dataset,
filtering out anything older than 50 years and anything published "after" 2024.
Then, calculate the number of years that have passed since their first publication. 
```{r}
# limit to the last 50 years and can't go into the future
prof_entry <- oa_distinct_pubs %>%
  filter(publication_year > 1974 & publication_year <= 2024)%>%
  group_by(profile_id)%>%
  slice(which.min(publication_year))%>%
  select(profile_id, publication_year)

colnames(prof_entry)[2] <- "entry"

prof_entry$years_since_entry <- 2024 - prof_entry$entry

prof_table <- merge(prof_table,
                    prof_entry,
                    by = "profile_id",
                    all.x = TRUE)
```

Assign professors into groups based on the years since their first publication in
our dataset - in groups of 10 years.
```{r}
prof_table$year_group <- cut(prof_table$years_since_entry, c(0, 10, 20, 30, 40, 50))
prof_table$year_group <- paste("up to", str_remove(str_split_i(prof_table$year_group, ",", 2), "\\]"))

men_profs_year_group <- filter(prof_table, inferred_gender == "m")
women_profs_year_group <- filter(prof_table, inferred_gender == "w")
```

And get averages per year group, per gender, to plot the means later.
```{r warning = F, message= F}
year_group_stats <- prof_table %>%
  filter(., !is.na(inferred_gender) & year_group != "up to NA")%>%
  group_by(year_group, inferred_gender)%>%
  summarise(
    n = n(),
    mean_pubs = mean(pubs_total),
    mean_coauthors = mean(coauthors_total),
    mean_attention = mean(attention_total))
```

# Year-group and gender table

Prepare the data and then manually get the table comparing means of different
age groups.
```{r}
year_group_stats_men <- men_profs_year_group %>%  
  filter(., !is.na(inferred_gender) & year_group != "up to NA")%>%
  group_by(year_group)%>%
  summarise(
    n = n(),
    mean_pubs = mean(pubs_total),
    mean_coauthors = mean(coauthors_total),
    mean_attention = mean(attention_total))

colnames(year_group_stats_men)[2:5] <- paste0(colnames(year_group_stats_men)[2:5], "_men")
  
year_group_stats_women <- women_profs_year_group %>%  
  filter(., !is.na(inferred_gender) & year_group != "up to NA")%>%
  group_by(year_group)%>%
  summarise(
    n = n(),
    mean_pubs = mean(pubs_total),
    mean_coauthors = mean(coauthors_total),
    mean_attention = mean(attention_total))

colnames(year_group_stats_women)[2:5] <- paste0(colnames(year_group_stats_women)[2:5], "_women")


# mean comparisons
categories <- c("up to 10", "up to 20", "up to 30", "up to 40", "up to 50")
pub_test <- c()
pub_stars <- c()
coauthor_test <- c()
coauthor_stars <- c()
news_att_test <- c()
news_att_stars <- c()
for(i in 1:length(categories)){
  cat <- categories[i]
  
  pub <- wilcox.test(filter(men_profs_year_group, year_group == cat)$pubs_total, 
                             filter(women_profs_year_group, year_group == cat)$pubs_total, 
                             alternative = "two.sided")
  
  pub_test[i] <- pub$p.value
  pub_stars[i] <- ifelse(pub$p.value <= 0.01, 
                         "***",
                         ifelse(pub$p.value <= 0.05,
                                "**",
                                ifelse(pub$p.value <= 0.1,
                                "*", "")))
  
  coauthor <- wilcox.test(filter(men_profs_year_group, year_group == cat)$coauthors_total, 
                             filter(women_profs_year_group, year_group == cat)$coauthors_total, 
                             alternative = "two.sided")
  
  coauthor_test[i] <- coauthor$p.value
  coauthor_stars[i] <- ifelse(coauthor$p.value <= 0.01, 
                              "***",
                              ifelse(coauthor$p.value <= 0.05,
                                     "**",
                                     ifelse(coauthor$p.value <= 0.1,
                                     "*", "")))
  
  attention <- wilcox.test(filter(men_profs_year_group, year_group == cat)$attention_total, 
                             filter(women_profs_year_group, year_group == cat)$attention_total, 
                             alternative = "two.sided")
  
  news_att_test[i] <- attention$p.value
  news_att_stars[i] <- ifelse(attention$p.value <= 0.01, 
                              "***",
                              ifelse(attention$p.value <= 0.05,
                                     "**",
                                     ifelse(attention$p.value <= 0.1,
                                     "*", "")))
  
  
  
}

full_table <- cbind.data.frame("Year group" = year_group_stats_men$year_group,
                               "N men" = year_group_stats_men$n_men,
                               "N women" = year_group_stats_women$n_women,
                               "% women" = year_group_stats_women$n_women / (year_group_stats_women$n_women + year_group_stats_men$n_men)*100,
                               "Avg. pub. men" = year_group_stats_men$mean_pubs_men,
                               "Avg. pub. women" = year_group_stats_women$mean_pubs_women,
                               "p" = pub_test,
                               "sig" = pub_stars,
                               "Avg. coauthor men" = year_group_stats_men$mean_coauthors_men,
                               "Avg. coauthor women" = year_group_stats_women$mean_coauthors_women,
                               "p coauthor" = coauthor_test,
                               "sig coauthor" = coauthor_stars,
                               "Avg. att. men" = year_group_stats_men$mean_attention_men,
                               "Avg. att. women" = year_group_stats_women$mean_attention_women,
                               "p attention" = news_att_test,
                               "sig attention" = news_att_stars)

full_table <- full_table %>%
  mutate(across(c("% women",
                  "Avg. pub. men", "Avg. pub. women",
                  "Avg. coauthor men", "Avg. coauthor women",
                  "Avg. att. men", "Avg. att. women"), \(x) round(x, 2)))%>%
  mutate(across(c("p", "p coauthor", "p attention"), \(x) round(x, 3)))

```

```{r fig.width = 12}
knitr::kable(full_table, caption = "Table 1. Means per year-entry group")
```


# Year-group and gender plots

## Total publications

```{r fig.width= 12, fig.heght = 8, cache = T}
prof_table %>%
  filter(year_group != "up to NA")%>%
ggplot(., aes(x=pubs_total, color=inferred_gender)) +
  geom_histogram(fill="white", position="dodge", bins = 40)+
  geom_vline(data=year_group_stats, aes(xintercept=mean_pubs, color=inferred_gender),
             linetype="dashed")+
  xlab("Total Publications")+
  ylab("Count")+
  labs(color='Inferred gender')+
  ggtitle("Histograms: publications per years since entry")+
  facet_wrap(. ~ year_group, nrow = 2)
```

2. Total coauthors - facet by the N years since first publication:

```{r fig.width= 12, fig.heght = 8, cache = T}
prof_table %>%
  filter(year_group != "up to NA")%>%
ggplot(., aes(x=coauthors_total, color=inferred_gender)) +
  geom_histogram(fill="white", position="dodge", bins = 40)+
  geom_vline(data=means_prof_table, aes(xintercept=mean_coauthors, color=inferred_gender),
             linetype="dashed")+
  xlab("Total Coauthors")+
  ylab("Count")+
  labs(color='Inferred gender')+
  ggtitle("Histograms: coauthors per years since entry")+
  facet_wrap(. ~ year_group, nrow = 2)
```
3. Total news mentions - facet by the N years since first publication:

```{r fig.width= 12, fig.heght = 8, cache = T, warning = F, message = F}
prof_table %>%
  filter(year_group != "up to NA")%>%
ggplot(., aes(x=attention_total, color=inferred_gender)) +
  geom_histogram(fill="white", position="dodge", bins = 40)+
  geom_vline(data=means_prof_table, aes(xintercept=mean_attention, color=inferred_gender),
             linetype="dashed")+
  xlim(0,1500)+
  ylim(0, 600)+
  xlab("Total Coauthors")+
  ylab("Count")+
  labs(color='Inferred gender')+
  ggtitle("Histograms: news attention per years since entry")+
  facet_wrap(. ~ year_group, nrow = 2)
```


## Per gender

Histograms of total publications, coauthors, and news attention.
```{r cache = T, fig.height = 9, fig.width=6}
p1 <- ggplot(prof_table, aes(x=pubs_total, color=inferred_gender)) +
  geom_histogram(fill="white", position="dodge", bins = 40)+
  geom_vline(data=means_prof_table, aes(xintercept=mean_pubs, color=inferred_gender),
             linetype="dashed")+
  xlab("Total Publications")+
  ylab("Count")+
  labs(color='Inferred gender')+
  ggtitle("Histograms: publications")

p2 <- ggplot(prof_table, aes(x=coauthors_total, color=inferred_gender)) +
  geom_histogram(fill="white", position="dodge", bins = 40)+
  geom_vline(data=means_prof_table, aes(xintercept=mean_coauthors, color=inferred_gender),
             linetype="dashed")+
  xlab("Total Coauthors")+
  ylab("Count")+
  labs(color='Inferred gender')+
  ggtitle("Histograms: coauthors")

p3 <- ggplot(prof_table, aes(x=attention_total, color=inferred_gender)) +
  geom_histogram(fill="white", position="dodge", bins = 40)+
  geom_vline(data=means_prof_table, aes(xintercept=mean_attention, color=inferred_gender),
             linetype="dashed")+
  xlab("Total News Mentions")+
  ylab("Count")+
  labs(color='Inferred gender')+
  ggtitle("Histograms: news attention")

ggarrange(p1, p2, p3, nrow = 3)
```

Box plots of total publications, coauthors, and news attention.
```{r cache = T, fig.height = 9, fig.width=6}
b1 <- ggboxplot(prof_table, x = "inferred_gender", y = "pubs_total", 
          color = "inferred_gender",
          ylab = "Average N publications", xlab = "Inferred gender")

b2 <- ggboxplot(prof_table, x = "inferred_gender", y = "coauthors_total", 
          color = "inferred_gender", 
          ylab = "Average N Coauthors", xlab = "Inferred gender")

b3 <- ggboxplot(prof_table, x = "inferred_gender", y = "attention_total", 
          color = "inferred_gender",
          ylab = "Average N news mentions", xlab = "Inferred gender")

ggarrange(b1, b2, b3, nrow = 3)
```



Mean comparisons.
```{r, cache = T}
print("total publications")
wilcox.test(men_profs$pubs_total, women_profs$pubs_total, alternative = "greater")

print("total coauthors")
wilcox.test(men_profs$coauthors_total, women_profs$coauthors_total, alternative = "greater")

print("total news mentions")
wilcox.test(men_profs$attention_total, women_profs$attention_total, alternative = "greater")
```
