---
title: "Untitled"
author: "Ana Macanovic"
date: "2024-01-29"
output: html_document
---

This script compiles our various data resources into a panel data of professors'
publications, citations, mentions, and coauthorships per year.

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

Load the packages:
```{r message=  F, warning = F, eval = T}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", "PerformanceAnalytics",
                      "tidyverse", "RPostgres", "lubridate", "psych",
                      "digest", "DBI", "RODBC", "odbc", "gridExtra",
                      "panelr", "skimr", "foreach", "vegan",
                      "doParallel")
groundhog.library(packages_to_load, date = "2023-12-01")

# load the helper function file
source("helper_functions.R")
```

Connect to the database:
```{r}
# fill in own credentials
port <- 
user <- ""
password <- ""
database_name <- ""

con <- RPostgres::dbConnect(RPostgres::Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)

con # Checks connection is working
```


Load the professor profiles:
```{r message = F, warning = F}
narcis_prof_info <- dbReadTable(con, "narcis_prof_info")
```

# Publications and citations

Load publication info for all professors:
```{r}
# all professors, their pubs, and the citations
oa_prof_pubs <- dbReadTable(con, "oa_prof_pubs")

# unique publication info
oa_pubs_unique <- dbReadTable(con, "oa_prof_pubs_unique")

#prof - pub matching
oa_prof_pub_matching <- dbReadTable(con, "oa_prof_pub_match")

# prof unique pub list 
oa_prof_pubs_unique <- merge(oa_pubs_unique,
                             oa_prof_pub_matching[c("id", "au_id", "au_display_name", "profile_id")],
                             all.x = TRUE,
                             all.y = TRUE,
                             by = "id")
```

Get single author publications only:
```{r}
coauthor_info <- dbGetQuery(con, "select \"id\", \"au_id\" FROM oa_coauthor_info;")

oa_prof_pubs_unique_single_au <- filter(oa_prof_pubs_unique, 
                                        ! id %in% coauthor_info$id)
```


Get yearly publication counts per professor, filtering out everything but articles,
books, book chapters:
```{r}
prof_year_pubs <- oa_prof_pubs_unique %>% 
  filter(!is.na(publication_year) & publication_year > 1974 & publication_year <= 2024 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id, publication_year)%>%
  summarise(count_pubs = n())%>%
  arrange(profile_id, publication_year)%>%
  mutate(count_pubs_total = cumsum(count_pubs))%>%
  arrange(profile_id, publication_year)

# rename for merging
colnames(prof_year_pubs)[which(colnames(prof_year_pubs) == "publication_year")] <- "year"
```
Now, get their yearly citations (2012-2024):
```{r}
prof_year_citations <- oa_prof_pubs %>% 
  filter(!is.na(publication_year) & !is.na(counts_by_year_year) & publication_year > 1974 & publication_year <= 2024 &
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id, counts_by_year_year)%>%
  summarise(cited_by = sum(counts_by_year_cited_by_count))%>%
  arrange(profile_id, counts_by_year_year) %>%
  mutate(cited_by_total_oa = cumsum(cited_by))%>%
  arrange(profile_id, counts_by_year_year)

# rename for merging
colnames(prof_year_citations)[which(colnames(prof_year_citations) == "counts_by_year_year")] <- "year"
```

Now, we want to know how many citations there were before 2012, so we get the totals
and then generate a new column getting the pre-2012 citations + each year's citations:
```{r}
# total citations per prof
prof_total_citations <- oa_prof_pubs_unique %>%
  filter(!is.na(publication_year) & publication_year > 1974 & publication_year <= 2024 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id)%>%
  summarise(cited_by_since_pub_2024 = sum(cited_by_count))
# rename for merging
colnames(prof_total_citations)[which(colnames(prof_total_citations) == "publication_year")] <- "year"


# get the citations preceding 2012 by deducting the 2012 citations from the total
latest_citation <- prof_year_citations %>%
  group_by(profile_id)%>%
  slice(which.max(year))

# merge these two, replace NAs
prof_total_citations <- merge(prof_total_citations,
                              latest_citation[c("profile_id", "cited_by_total_oa")],
                              by = "profile_id",
                              all.x = TRUE,
                              all.y = TRUE)

prof_total_citations <- prof_total_citations %>%
  replace(is.na(.), 0)

# get the citation count for profs before 2012
prof_total_citations$cited_by_before_2012 <- prof_total_citations$cited_by_since_pub_2024 - prof_total_citations$cited_by_total_oa
  
# merge this with citation data
prof_year_citations <- merge(prof_year_citations,
                             prof_total_citations[c("profile_id", "cited_by_before_2012")],
                             all.x = TRUE,
                             by = "profile_id")

# get cumulative citations of pre 2012 + the year in question
prof_year_citations$cited_by_total_all <- prof_year_citations$cited_by_total_oa + prof_year_citations$cited_by_before_2012


# combine publication counts and citation counts, filling gaps with NAs
prof_year_pubs_citations <- merge(prof_year_pubs,
                                  prof_year_citations,
                                  all.x = TRUE,
                                  all.y = TRUE,
                                  by = c("profile_id", "year"))

# fill some NAs for publication counts, but we will not do this for citations
prof_year_pubs_citations$count_pubs <- ifelse(is.na(prof_year_pubs_citations$count_pubs),
                                              0,
                                              prof_year_pubs_citations$count_pubs)

# fill the total gaps down for cumulative publications
prof_year_pubs_citations <- prof_year_pubs_citations %>%
  group_by(profile_id)%>%
  fill(count_pubs_total)

# fill the citations before 2012
prof_year_pubs_citations <- prof_year_pubs_citations %>%
  group_by(profile_id)%>%
  fill(cited_by_before_2012, .direction = "up")

```

For each prof, get the first publication year and merge with the rest:
```{r}
# get professor entry years
prof_entry_year <- oa_prof_pubs_unique %>%
  filter(publication_year > 1974 & publication_year <= 2024 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id)%>%
  slice(which.min(publication_year))%>%
  select(profile_id, publication_year)

# rename
colnames(prof_entry_year)[2] <- "first_pub"

# merge
prof_year_pubs_citations <- merge(prof_year_pubs_citations,
                                  prof_entry_year,
                                  all.x = TRUE,
                                  by = "profile_id")

# get indicator of years since first pub
prof_year_pubs_citations$years_since_first_pub <- prof_year_pubs_citations$year - prof_year_pubs_citations$first_pub
```

Merge this with professor gender:
```{r}
prof_gender <- dbReadTable(con, "gender_table")

prof_year_pubs_citations <- merge(prof_year_pubs_citations,
                                  prof_gender[c("profile_id", "inferred_gender")],
                                  all.x = TRUE,
                                  by = "profile_id")
```

# Grant information

Get all the grant information:
```{r}
nwo_grants <- dbReadTable(con, "narcis_nwo_grant_info")
erc_grants <- dbReadTable(con, "erc_grant_info")
```

Get this into a binary format:
```{r}
# for NWO
nwo_grants$veni <- ifelse(nwo_grants$grant == "veni", 1, 0)
nwo_grants$vidi <- ifelse(nwo_grants$grant == "vidi", 1, 0)
nwo_grants$vici <- ifelse(nwo_grants$grant == "vici", 1, 0)
nwo_grants$spinoza <- ifelse(nwo_grants$grant == "spinoza", 1, 0)
nwo_grants$stevin <- ifelse(nwo_grants$grant == "stevin", 1, 0)
# select only the necessary columns
nwo_grants <- nwo_grants %>%
  select(year:stevin)

# for ERC
erc_grants$advanced <- ifelse(erc_grants$grant == "Advanced grants", 1, 0)
erc_grants$consolidator <- ifelse(erc_grants$grant == "Consolidator grants", 1, 0)
erc_grants$starting  <- ifelse(erc_grants$grant == "Starting grants", 1, 0)
erc_grants$synergy <- ifelse(erc_grants$grant == "Synergy grants", 1, 0)
# select only the necessary columns
erc_grants <- erc_grants %>%
  select(profile_id:synergy)
```


Combine this with pubs and citations
```{r}
prof_year_pubs_citations_grants <- merge(prof_year_pubs_citations,
                                         nwo_grants,
                                         all.x = TRUE,
                                         by = c("profile_id", "year"))

prof_year_pubs_citations_grants <- merge(prof_year_pubs_citations_grants,
                                         erc_grants,
                                         all.x = TRUE,
                                         by = c("profile_id", "year"))

# replace NAs
prof_year_pubs_citations_grants <- prof_year_pubs_citations_grants %>%
  mutate_at(vars(veni:synergy), ~replace_na(., 0))
```


# Altmetric attention

Get all the attention measures we have per paper:
```{r}
attention_news <- dbReadTable(con, "altmetric_pub_att_news")
attention_blogs <- dbReadTable(con, "altmetric_pub_att_blogs")

# merge the papers with their authors
attention_news_profs <- merge(attention_news,
                        oa_prof_pub_matching[c("id", "profile_id")],
                        by = "id")

# merge the papers with their authors
attention_blogs_profs <- merge(attention_blogs,
                        oa_prof_pub_matching[c("id", "profile_id")],
                        by = "id")
```

Compile the attention per professor per year:
```{r}
# get a year from the "posted on" string
attention_news_profs$year <- year(as_date(attention_news_profs$posted_on))
attention_blogs_profs$year <- year(as_date(attention_blogs_profs$posted_on))

prof_year_attention_news <- attention_news_profs %>%
  group_by(profile_id, year)%>%
  summarise(attn_news_by = n())%>%
  arrange(profile_id, year) %>%
  mutate(attn_news_by_total = cumsum(attn_news_by)) %>%
  arrange(profile_id, year)


prof_year_attention_blogs <- attention_blogs_profs %>%
  group_by(profile_id, year)%>%
  summarise(attn_blogs_by = n())%>%
  arrange(profile_id, year) %>%
  mutate(attn_blogs_by_total = cumsum(attn_blogs_by)) %>%
  arrange(profile_id, year)
```
Merge the attention with the rest: 
```{r}
prof_year_p_c_g_a <- merge(prof_year_pubs_citations_grants,
                           prof_year_attention_news,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

# fill down
prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  group_by(profile_id)%>%
  fill(attn_news_by_total)

prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_blogs,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  group_by(profile_id)%>%
  fill(attn_blogs_by_total)
```

Combine this with Twitter attention, which we only obtain using ORCIDs (for now).
```{r}
twitter_orcid_attention <- dbGetQuery(con, statement = "select * from altmetric_prof_attention where \"mention_type\"='tweet'")

# rename the columns and get cumulatives
twitter_orcid_attention <- twitter_orcid_attention %>%
  select(profile_id, year, yearly_count)

colnames(twitter_orcid_attention)[which(colnames(twitter_orcid_attention) == "yearly_count")] <- "attn_twitter_by"

prof_year_attention_twitter <- twitter_orcid_attention %>%
  arrange(profile_id, year)%>%
  group_by(profile_id)%>%
  mutate(attn_twitter_by_total = cumsum(attn_twitter_by)) %>%
  arrange(profile_id, year)

prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_twitter,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  group_by(profile_id)%>%
  fill(attn_twitter_by_total)
```

As Atlmetric data goes back to 2011, set attention to 0 if year >= 2011, leave as NA
otherwise:
```{r}
prof_year_p_c_g_a$attn_blogs_by <- ifelse((is.na(prof_year_p_c_g_a$attn_blogs_by) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_blogs_by)

prof_year_p_c_g_a$attn_blogs_by_total <- ifelse((is.na(prof_year_p_c_g_a$attn_blogs_by_total) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_blogs_by_total)

prof_year_p_c_g_a$attn_news_by <- ifelse((is.na(prof_year_p_c_g_a$attn_news_by) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_news_by)

prof_year_p_c_g_a$attn_news_by_total <- ifelse((is.na(prof_year_p_c_g_a$attn_news_by_total) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_news_by_total)

prof_year_p_c_g_a$attn_twitter_by <- ifelse((is.na(prof_year_p_c_g_a$attn_twitter_by) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_twitter_by)

prof_year_p_c_g_a$attn_twitter_by_total <- ifelse((is.na(prof_year_p_c_g_a$attn_twitter_by_total) & prof_year_p_c_g_a$year >=  2011),
                                            0,
                                            prof_year_p_c_g_a$attn_twitter_by_total)
```


## Main field
Get each professor's main field in a given year based on their papers, and get 
their overall specialization.

First, fethcing the topics: 
```{r}
oa_pubs_topics <- dbReadTable(con, "oa_pubs_topics")

oa_pubs_topics <- merge(oa_prof_pub_matching,
                        oa_pubs_topics,
                        by = "id",
                        all.x = TRUE)

oa_pubs_topics <- merge(oa_pubs_topics,
                        oa_pubs_unique[c("id", "publication_year")],
                        by = "id")
```

Professor's topic diversity per year:
```{r}
oa_pubs_topics2 <- oa_pubs_topics
oa_pubs_topics2$field_display_name <- as.factor(oa_pubs_topics2$field_display_name)

prof_year_field <- oa_pubs_topics2 %>%
  group_by(profile_id, publication_year, field_display_name) %>%
  summarise(n = n())%>%
  filter(!is.na(field_display_name))
  pivot_wider(names_from = field_display_name, values_from = n)%>%
  replace(is.na(.), 0)
  

div_indices <- diversity(prof_year_field[, -c(1:2)], index = "shannon")

prof_year_field_div <- cbind.data.frame(prof_year_field[, c(1:2)],
                                        yearly_diversity = div_indices)

prof_year_field_div$yarly_evennes <- prof_year_field_div$yearly_diversity/log(27)
```



Fields and subfields per prof per year and in total
```{r}
prof_year_field <- oa_pubs_topics %>%
  group_by(profile_id, publication_year, field_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_year_field)[c(2,3)] <- c("year","yearly_field" )

prof_total_field <- oa_pubs_topics %>%
  group_by(profile_id, field_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_total_field)[2] <- c("overall_field" )


prof_year_subfield <- oa_pubs_topics %>%
  group_by(profile_id, publication_year, subfield_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_year_subfield)[c(2,3)] <- c("year","yearly_subfield") 


prof_total_subfield <- oa_pubs_topics %>%
  group_by(profile_id, subfield_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_total_subfield)[2] <- c("overall_subfield" )

# merge profs and their fields
prof_year_p_c_g_a_t <- merge(prof_year_p_c_g_a,
                             prof_year_field[c("profile_id", "yearly_field", "year")],
                             by = c("profile_id", "year"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_t <- merge(prof_year_p_c_g_a_t,
                             prof_year_subfield[c("profile_id", "yearly_subfield", "year")],
                             by = c("profile_id", "year"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_t <- merge(prof_year_p_c_g_a_t,
                             prof_total_field[c("profile_id", "overall_field")],
                             by = c("profile_id"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_t <- merge(prof_year_p_c_g_a_t,
                             prof_total_subfield[c("profile_id", "overall_subfield")],
                             by = c("profile_id"),
                             all.x = TRUE,
                             all.y = FALSE) 
```

Remove duplicates, if any:
```{r}
prof_year_p_c_g_a_t$dupl <- duplicated(prof_year_p_c_g_a_t[c("profile_id", "year")])

prof_year_p_c_g_a_t <- prof_year_p_c_g_a_t %>%
  filter(dupl == FALSE)%>%
  select(-dupl)
```

```{r}
write_csv(prof_year_p_c_g_a_t, "panel_datasets/prof_year_p_c_g_a_t_11_3.csv")
```


Remove some redundant objects:
```{r}
rm(oa_prof_pubs)
rm(oa_pubs_topics)
rm(oa_pubs_unique)
gc()
```

Get the lagged variables.

Add placeholder variables for lagged sales and revenues:
```{r}
prof_year_p_c_g_a_t_l <- prof_year_p_c_g_a_t

prof_year_p_c_g_a_t_l$count_pubs_l <- prof_year_p_c_g_a_t_l$count_pubs
prof_year_p_c_g_a_t_l$count_pubs_total_l <- prof_year_p_c_g_a_t_l$count_pubs_total
prof_year_p_c_g_a_t_l$cited_by_l <- prof_year_p_c_g_a_t_l$cited_by
prof_year_p_c_g_a_t_l$cited_by_total_oa_l <- prof_year_p_c_g_a_t_l$cited_by_total_oa
prof_year_p_c_g_a_t_l$cited_by_total_all_l <- prof_year_p_c_g_a_t_l$cited_by_total_all
prof_year_p_c_g_a_t_l$attn_news_by_l <- prof_year_p_c_g_a_t_l$attn_news_by
prof_year_p_c_g_a_t_l$attn_news_by_total_l <- prof_year_p_c_g_a_t_l$attn_news_by_total
prof_year_p_c_g_a_t_l$attn_blogs_by_l <- prof_year_p_c_g_a_t_l$attn_blogs_by
prof_year_p_c_g_a_t_l$attn_blogs_by_total_l <- prof_year_p_c_g_a_t_l$attn_blogs_by_total
prof_year_p_c_g_a_t_l$attn_twitter_by_l <- prof_year_p_c_g_a_t_l$attn_twitter_by
prof_year_p_c_g_a_t_l$attn_twitter_by_total_l <- prof_year_p_c_g_a_t_l$attn_twitter_by_total

prof_year_p_c_g_a_t_l$veni_l <- prof_year_p_c_g_a_t_l$veni
prof_year_p_c_g_a_t_l$vidi_l <- prof_year_p_c_g_a_t_l$vidi
prof_year_p_c_g_a_t_l$vici_l <- prof_year_p_c_g_a_t_l$vici
prof_year_p_c_g_a_t_l$stevin_l <- prof_year_p_c_g_a_t_l$stevin
prof_year_p_c_g_a_t_l$spinoza_l <- prof_year_p_c_g_a_t_l$spinoza

prof_year_p_c_g_a_t_l$advanced_l <- prof_year_p_c_g_a_t_l$advanced
prof_year_p_c_g_a_t_l$consolidator_l <- prof_year_p_c_g_a_t_l$consolidator
prof_year_p_c_g_a_t_l$starting_l <- prof_year_p_c_g_a_t_l$starting
prof_year_p_c_g_a_t_l$synergy_l <- prof_year_p_c_g_a_t_l$synergy
```

Rearrange the variables:
```{r}
lag_rearrange <- c("profile_id", "year", "inferred_gender",
                   "first_pub", "years_since_first_pub",
                   "yearly_field", "yearly_subfield",    
                   "overall_field", "overall_subfield",
                   "count_pubs", "count_pubs_l",  
                   "count_pubs_total", "count_pubs_total_l",
                   "cited_by", "cited_by_l",
                   "cited_by_total_oa", "cited_by_total_oa_l", 
                   "cited_by_before_2012",
                   "cited_by_total_all", "cited_by_total_all_l",
                   "attn_news_by", "attn_news_by_l",
                   "attn_news_by_total", "attn_news_by_total_l",
                   "attn_blogs_by", "attn_blogs_by_l",
                   "attn_blogs_by_total", "attn_blogs_by_total_l", 
                   "attn_twitter_by", "attn_twitter_by_l",
                   "attn_twitter_by_total", "attn_twitter_by_total_l",
                   "veni", "veni_l",
                   "vidi", "vidi_l",
                   "vici", "vici_l",
                   "stevin", "stevin_l",
                   "spinoza", "spinoza_l",
                   "starting", "starting_l",
                   "advanced", "advanced_l", 
                   "consolidator", "consolidator_l",
                   "synergy", "synergy_l"
                   )

prof_year_p_c_g_a_t_l <- prof_year_p_c_g_a_t_l[lag_rearrange]
```

Lag the relevant variables:
```{r}
prof_year_p_c_g_a_t_l <- prof_year_p_c_g_a_t_l %>%
  arrange(year) %>%
  group_by(profile_id) %>%
  mutate_at(vars(contains('_l')), lag)%>%
  arrange(profile_id, year)
```

```{r}
write_csv(prof_year_p_c_g_a_t_l, "panel_datasets/prof_year_p_c_g_a_t_l_11_3.csv")
```


# Lexis data

Load the lexis articles, filter out the irrelevant ones and drop the regional
publication duplicates:
```{r}
lexis_data <- dbReadTable(con, "lexis_nexis_mentions")

lexis_data_filt <- filter(lexis_data,
                          source_type != "irrelevant")

lexis_data_filt$dupl <- duplicated(lexis_data_filt[c("profile_id", "headline", "length")])

lexis_data_filt <- lexis_data_filt %>%
  filter(dupl == FALSE)%>%
  select(-dupl)
```

Now, aggregate professor mentions per year and per source, wherever relevant:
```{r}
# combine sources for easier handling:
lexis_data_filt$source_coarse <- ifelse(! lexis_data_filt$source_type %in% c("national_nl", "regional_nl", "high_prof_intl"),
                                        "other",
                                        lexis_data_filt$source_type)

prof_lexis_year <- lexis_data_filt %>%
  filter(!is.na(year) & year >= 1974 & year <= 2024)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id, year, source_coarse)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year,source_coarse)%>%
  group_by(profile_id, source_coarse)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_coarse, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

# tidy up the columns
colnames(prof_lexis_year)[3:10] <- c("lexis_national", "lexis_regional", "lexis_other",
                                     "lexis_intl", "lexis_national_total", 
                                     "lexis_regional_total", "lexis_other_total",
                                     "lexis_intl_total")

# add total counts
prof_lexis_year$lexis_all <- prof_lexis_year$lexis_national + prof_lexis_year$lexis_regional +
  prof_lexis_year$lexis_other + prof_lexis_year$lexis_intl

prof_lexis_year$lexis_all_total <- prof_lexis_year$lexis_national_total + prof_lexis_year$lexis_regional_total +
  prof_lexis_year$lexis_other_total + prof_lexis_year$lexis_intl_total

# rearrange a bit
prof_lexis_year <- prof_lexis_year[c("profile_id", "year",
                                     "lexis_national", "lexis_regional", "lexis_other",
                                     "lexis_intl", "lexis_all",
                                     "lexis_national_total", 
                                     "lexis_regional_total", "lexis_other_total",
                                     "lexis_intl_total", "lexis_all_total")]
```

Pad lexis data with the professor panel:
```{r}
# get all observations in the panel
prof_lexis_year_pad <- merge(prof_lexis_year,
                             prof_year_p_c_g_a_t_l[c("profile_id", "year")],
                             all.y= TRUE,
                             all.x = TRUE)

# fill down on totals and replace NAs with zeroes
prof_lexis_year_pad <- prof_lexis_year_pad %>%
  group_by(profile_id)%>%
  fill(lexis_national_total:lexis_all_total, .direction = "down")%>%
  mutate(across(contains('lexis'), replace_na, 0))

# get the first lab
prof_lexis_year_pad_lag <- prof_lexis_year_pad %>%
  arrange(year) %>%
  group_by(profile_id) %>%
  mutate_at(vars(contains('lexis')), lag)%>%
  arrange(profile_id, year)

colnames(prof_lexis_year_pad_lag)[-c(1:2)] <- paste0(colnames(prof_lexis_year_pad_lag)[-c(1:2)], "_l")
```

Combine the two:
```{r}
prof_lexis_year_all <- merge(prof_lexis_year_pad,
                             prof_lexis_year_pad_lag,
                             by = c("profile_id", "year"))
```


Combine our professor panel with lexis data:
```{r}
prof_year_p_c_g_a_t_l_l <- merge(prof_year_p_c_g_a_t_l,
                                 prof_lexis_year_all,
                                 by = c("profile_id", "year"),
                                 all.x = TRUE)
```

Write this out:
```{r}
write_csv(prof_year_p_c_g_a_t_l_l, "panel_datasets/prof_year_p_c_g_a_t_l_l_20_3.csv")
```

# Coauthor data

Fetch all coauthor data, including full info, their inferred gender, and citation counts.
```{r}
oa_coauthor_info <- dbReadTable(con, "oa_coauthor_info")
oa_coauthor_info_name <- dbReadTable(con, "oa_coauthor_name_list")
coauthor_gender <- dbReadTable(con, "coauthor_name_gender")
# add professor gender names, as these are specific for the 
# Dutch context and might help further
prof_gender_names <- dbReadTable(con, "gender_table")%>%
  distinct(first, .keep_all = TRUE)%>%
  select(first, inferred_gender)
oa_coauthor_info_full <- dbReadTable(con, "oa_coauthor_info_full")
```

Match name gender inference with coauthor names:
```{r}
colnames(coauthor_gender)[2] <- "first"
coauthor_gender <- coauthor_gender %>%
  filter(first != "")%>%
  select(first, gender)

# recode the variable
coauthor_gender$gender <- ifelse(coauthor_gender$gender == "male", "m",
                                 ifelse(coauthor_gender$gender == "female", "w", coauthor_gender$gender))

colnames(prof_gender_names)[2] <- "gender"

# combine
all_names <- rbind(coauthor_gender,
                   prof_gender_names)%>%
  distinct(first, .keep_all = TRUE)


# filter out "and" which seems to just be a mistake
oa_coauthor_info_name <- oa_coauthor_info_name %>%
  filter(! tolower(first) %in% c("van", "and", "den"))

oa_coauthor_info_name$first <- tolower(oa_coauthor_info_name$first)

coauthor_name_gender <- merge(oa_coauthor_info_name,
                              all_names,
                              by = "first",
                              all.x = TRUE,
                              all.y = FALSE)

coauthor_name_gender <- coauthor_name_gender %>%
  select(id, gender)%>%
  filter(!is.na(gender))

```

Remove redundant items:
```{r}
#rm(oa_coauthor_info)
gc()
```

For each coauthor, get their cumulative citation counts:
```{r}
coauthor_pubs_cits_cumulative <- oa_coauthor_info_full %>%
  select(id:display_name, works_count:counts_by_year_cited_by_count)%>%
  group_by(id)%>%
  arrange(counts_by_year_year)%>%
  mutate(counts_by_year_works_count_total = cumsum(counts_by_year_works_count),
         counts_by_year_cited_by_count_total = cumsum(counts_by_year_cited_by_count)) %>%
  arrange(id, counts_by_year_year)

# rename some columns
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_year")] <- "year"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_works_count")] <- "count_pubs"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="works_count")] <- "count_pubs_total"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_works_count_total")] <- "count_pubs_total_oa"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_cited_by_count")] <- "cited_by"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="cited_by_count")] <- "cited_by_total"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_cited_by_count_total")] <- "cited_by_total_oa"

# citations prior to 2012
latest_citation_coauthor <- coauthor_pubs_cits_cumulative %>%
  group_by(id)%>%
  slice(which.max(year))
latest_citation_coauthor$cited_by_before_2012 <- latest_citation_coauthor$cited_by_total - latest_citation_coauthor$cited_by_total_oa
latest_citation_coauthor$count_pubs_before_2012 <- latest_citation_coauthor$count_pubs_total - latest_citation_coauthor$count_pubs_total_oa
# replace by 0 if negative (OA issue ticket opened)
latest_citation_coauthor$cited_by_before_2012 <- ifelse(latest_citation_coauthor$cited_by_before_2012<0,
                                                        0,
                                                        latest_citation_coauthor$cited_by_before_2012)

latest_citation_coauthor$count_pubs_before_2012 <- ifelse(latest_citation_coauthor$count_pubs_before_2012<0,
                                                        0,
                                                        latest_citation_coauthor$count_pubs_before_2012)

# merge with the rest
coauthor_pubs_cits_cumulative <- merge(coauthor_pubs_cits_cumulative,
                         latest_citation_coauthor[c("id", "cited_by_before_2012", "count_pubs_before_2012")],
                         by = "id",
                         all.x = TRUE)

coauthor_pubs_cits_cumulative$cited_by_total_all <- coauthor_pubs_cits_cumulative$cited_by_before_2012 + coauthor_pubs_cits_cumulative$cited_by_total_oa
coauthor_pubs_cits_cumulative$count_pubs_total_all <- coauthor_pubs_cits_cumulative$count_pubs_before_2012 + coauthor_pubs_cits_cumulative$count_pubs_total_oa

coauthor_year_p_c <- coauthor_pubs_cits_cumulative %>%
  arrange(id, year)%>%
  select(-display_name, -count_pubs_total, -cited_by_total)
```

Get their attention:
```{r}
coauthor_attention <- dbReadTable(con, "altmetric_coauthor_attention")

selected_attention <- coauthor_attention %>%
  filter(., mention_type %in% c("msm", "blog", "tweet"))
```

Cumulatives:
```{r}
coauthor_attention_table <- selected_attention %>%
  pivot_wider(names_from = mention_type, values_from = yearly_count, values_fill = 0)

coauthor_attention_table <- coauthor_attention_table %>%
  group_by(id)%>%
  arrange(year)%>%
  mutate(msm_total = cumsum(msm),
         blog_total = cumsum(blog),
         tweet_total = cumsum(tweet)) %>%
  arrange(id, year)

# rename some columns
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="msm")] <- "coa_attn_news_by"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="msm_total")] <- "coa_attn_news_by_total"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="blog")] <- "coa_attn_blog_by"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="blog_total")] <- "coa_attn_blog_by_total"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="tweet")] <- "coa_attn_twitter_by"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="tweet_total")] <- "coa_attn_twitter_by_total"
```

Combine citations and attention. Set mentions to 0 if we have coauthors' ORCID 
and there are no mentions; if we don't have their ORCID, set mentions to NA:
```{r}
coauthor_year_p_c_a <- merge(coauthor_year_p_c,
                             coauthor_attention_table,
                             by = c("id", "year"),
                             all.x = TRUE)

coauthor_orcids <- oa_coauthor_info_full %>%
  distinct(id, .keep_all = TRUE)%>%
  select(id, orcid)


coauthor_year_p_c_a <- merge(coauthor_year_p_c_a,
                             coauthor_orcids,
                             all.x = TRUE,
                             by = "id")

# fill the attention by profile ID
coauthor_year_p_c_a2 <- coauthor_year_p_c_a %>%
  group_by(id)%>%
  fill(coa_attn_news_by_total, coa_attn_blog_by_total, coa_attn_twitter_by_total)

coauthor_year_p_c_a2$coa_attn_news_by <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_news_by) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_news_by)
coauthor_year_p_c_a2$coa_attn_news_by_total <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_news_by_total) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_news_by_total)

coauthor_year_p_c_a2$coa_attn_blog_by <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_blog_by) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_blog_by)
coauthor_year_p_c_a2$coa_attn_blog_by_total <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_blog_by_total) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_blog_by_total)

coauthor_year_p_c_a2$coa_attn_twitter_by <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_twitter_by) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_twitter_by)
coauthor_year_p_c_a2$coa_attn_twitter_by_total <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_twitter_by_total) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_twitter_by_total)
```

Append gender:
```{r}
colnames(coauthor_name_gender)[1] <- "id"

coauthor_year_p_c_a_g <- merge(coauthor_year_p_c_a2,
                               coauthor_name_gender,
                               by = "id",
                               all.x = TRUE)

coauthor_year_p_c_a_g <- coauthor_year_p_c_a_g%>%
  arrange(id, year)

write_csv(coauthor_year_p_c_a_g, "panel_datasets/coauthor_year_p_c_a_g_11_3.csv")
```

Filter out coauthor observations without year:
```{r}
coauthor_year_p_c_a_g <- filter(coauthor_year_p_c_a_g, 
                                !is.na(year))%>%
  select(-dupl)
```

Marge coauthors with inferred gender:
```{r}
colnames(coauthor_name_gender) <- c("au_id", "inferred_gender")
oa_coauthor_info_gender <- merge(oa_coauthor_info,
                                 coauthor_name_gender,
                                 all.x = TRUE,
                                 by = "au_id")

oa_coauthor_info_gender$inferred_gender <- ifelse(is.na(oa_coauthor_info_gender$inferred_gender),
                                                  "unknown",
                                                  oa_coauthor_info_gender$inferred_gender)
```

Clean the memory a bit:
```{r}
rm(oa_coauthor_info)
rm(coauthor_name_gender)
rm(coauthor_gender)
rm(all_names)
gc()
```


For each author, match their coauthors from that year:
```{r}
oa_coauthor_matching <- dbReadTable(con, "oa_coauthor_matching")
oa_coauthor_matching <- oa_coauthor_matching[c("id", "au_id", "profile_id", "publication_year")]

profile_ids <- unique(prof_year_p_c_g_a_t_l_l$profile_id)
```

Now, compile coauthor data for each professor:
```{r warning = F, message = F}
prof_panel_combined <- as.data.frame(matrix(NA, nrow = 0, ncol = 118))

for (i in 1:length(profile_ids)){
  prof_output <- NA
  try(
    prof_output <- coauthor_data_compiler(profile_id = profile_ids[i],
                                          prof_panel = prof_year_p_c_g_a_t_l_l,
                                          prof_coauthor_matching = oa_coauthor_matching,
                                          prof_coauthor_panel = coauthor_year_p_c_a_g,
                                          prof_coauthor_info_w_gender = oa_coauthor_info_gender))

 
  if (!all(is.na(prof_output))){
    
    prof_panel_combined <- rbind.data.frame(prof_panel_combined,
                                            prof_output)
  }
  print(paste("done with ", i , " out of", length(profile_ids)))
}
```

