---
title: "Prof_gender"
author: "Ana Macanovic"
date: "2023-12-19"
---

This script checks assigns professor names as male or female. 
Because there are no self-reports of gender in the Narcis database, 
we infer a professor's gender from the first name filed in the database using
Genderize.io API.

```{r include = F}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

Load the libraries that we need:
```{r warning = F, message = F, eval = T}
library(groundhog)
packages_to_load <- c("readr", "dplyr", 
                      "stringr",
                      "digest",
                      "jsonlite")
groundhog.library(packages_to_load, date = "2023-12-01")
```

# Tidy up professor data from NARCIS

Load the professor profiles:
```{r message = F, warning = F, eval = F}
load("raw_data/media_profs_profiles.rda")
profs <- read_csv("raw_data/dutch_profs_urls.csv")

# merge the profs with their ORCIDs
colnames(profs)[c(1,7)] <- c("id", "profile_id")

profs_full <- merge(profs,
                    metadf[, c(1:4, 361)],
                    by = "profile_id")
```

# Define a function for gender inference
```{r eval = F}
genderize_io_function <- function(name,
                                  api_key = "",
                                  country_id = ""){
  # call the api using the name
  name_call <- paste0("https://api.genderize.io?name=", name)
  
  # if country ID provided
  if (country_id != ""){
    name_call <- paste0(name_call, "&country_id=", toupper(country_id))
  }
  # if API key provided
  if (api_key !=""){
    name_call <- paste0(name_call, "&apikey=", api_key, "")
  }
  output <- fromJSON(txt=name_call)
  # if no gender predicted
  if(is.null(output[["gender"]])){
    output[["gender"]] <- NA
  }
  output <- data.frame(output)
  return(output)
}
```


# Inferring gender
```{r warning = F, message = F, eval = F}
# fill in own api key
genderize_api_key <- ''

# list of names
names <- unique(profs_full$first)

prof_name_gender <- data.frame(matrix(NA, nrow = 0, ncol = 4))

for (i in 1:length(names)){
  name <- names[i]
  output <- genderize_io_function(name,
                      api_key = genderize_api_key,
                      country_id = "NL")
  
  prof_name_gender <- rbind(prof_name_gender,
                            output)
  print(paste("done with", i, "out of", length(names)))
}
```

Bind to prof data:
```{r eval = F}
# tidy up the colnames
colnames(prof_name_gender)[2] <- "first"

# merge the prof data with gender inference
profs_full_gender <- merge(profs_full,
                           prof_name_gender,
                           by = "first", 
                           all.x = TRUE)

# reorder the columns back
colnames_rearrange <- c(colnames(profs_full), colnames(prof_name_gender)[-2])
profs_full_gender <- profs_full_gender[colnames_rearrange]

# write this out
#saveRDS(profs_full_gender, "processed_data/profs_full_gender.RDS")
#write_csv(profs_full_gender, "processed_data/profs_full_gender.csv")
```

# Plots 

```{r eval = TRUE}
profs_full_gender <- readRDS("processed_data/profs_full_gender.RDS")
```


Plot the proportions:
```{r eval = TRUE}
ggplot(profs_full_gender) + 
  geom_bar(mapping = aes(x = gender, y = after_stat(prop), group = 1), stat = "count")
```


Plot the counts:
```{r eval = TRUE}
ggplot(profs_full_gender, aes(format(gender))) +
    geom_bar(stat = "count") +
    labs(x = "Number")
```


