---
title: "Untitled"
author: "Ana Macanovic"
date: "2024-02-29"
---

```{r}
options(width = 120)
knitr::opts_chunk$set(cache = FALSE, cache.lazy = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```


Load the packages:
```{r message=  F, warning = F, eval = T}
library(groundhog)
packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "tidyverse", "RPostgres", "lubridate", "psych",
                      "gridExtra", "DescTools",
                      "panelr", "skimr", "car","ggeffects",
                      "lmtest", "sandwich",
                      "stargazer","plm")
groundhog.library(packages_to_load, date = "2023-12-01")

```

# Data preparation

Load the panel:
```{r warning = F, message = F}
prof_panel <- read_csv("panel_datasets/prof_year_p_c_g_a_t_l_l_18_3.csv")
prof_panel_coa <- read_csv("panel_datasets/prof_panel_combined_no_lexis_19_3.csv")

# combine the two, since the latter mixes nexis data
lexis_data <- prof_panel %>%
  select(profile_id, year, contains("lexis"))

prof_panel_coa <- merge(prof_panel_coa,
                        lexis_data,
                        by= c("profile_id", "year"))

# recode the fields
prof_panel_coa <- prof_panel_coa %>% 
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))

prof_panel_coa <- prof_panel_coa %>% 
  mutate(general_field_yearly = case_match(
    yearly_field,
    "Arts and Humanities"  ~ "Arts & Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))
```
 
Rename the columns neatly:
```{r}
prof_panel_tidy <- prof_panel_coa %>%
  select(-c(cited_by_before_2012, cited_by_total_oa, cited_by_total_oa_l, dupl, dupl_l, 
           coa_cited_by_before_2012, coa_count_pubs_before_2012, coa_cited_by_before_2012_l,
           coa_count_pubs_before_2012, prof_tot_count_pubs_total_oa, prof_tot_cited_by_total_oa,
           prof_tot_cited_by_before_2012, prof_tot_count_pubs_before_2012  ))%>%
  rename(
    online_news = attn_news_by,
    online_news_total = attn_news_by_total,
    online_news_l = attn_news_by_l,
    online_news_total_l = attn_news_by_total_l,
    blogs = attn_blogs_by,
    blogs_total = attn_blogs_by_total,
    blogs_l = attn_blogs_by_l,
    blogs_total_l = attn_blogs_by_total_l,
    twitter = attn_twitter_by,
    twitter_total = attn_twitter_by_total,
    twitter_l = attn_twitter_by_l,
    twitter_total_l = attn_twitter_by_total_l,
    grant_veni = veni,
    grant_veni_l = veni_l,
    grant_vidi = vidi,
    grant_vidi_l = vidi_l,    
    grant_vici = vici,
    grant_vici_l = vici_l,
    grant_stevin = stevin,
    grant_stevin_l = stevin_l,
    grant_spinoza = spinoza,
    grant_spinoza_l = spinoza_l,
    grant_starting = starting,
    grant_starting_l = starting_l,
    grant_advanced = advanced,
    grant_advanced_l = advanced_l,
    grant_consolidator = consolidator,
    grant_consolidator_l = consolidator_l,
    grant_synergy = synergy,
    grant_synergy_l = synergy_l,
    coa_online_news = coa_attn_news_by,
    coa_blogs = coa_attn_blog_by,
    coa_twitter = coa_attn_twitter_by,
    coa_online_news_total = coa_attn_news_by_total,
    coa_blogs_total = coa_attn_blog_by_total,
    coa_twitter_total = coa_attn_twitter_by_total,
    coa_online_news_l = coa_attn_news_by_l,
    coa_blogs_l = coa_attn_blog_by_l,
    coa_twitter_l = coa_attn_twitter_by_l,
    coa_online_news_total_l = coa_attn_news_by_total_l,
    coa_blogs_total_l = coa_attn_blog_by_total_l,
    coa_twitter_total_l = coa_attn_twitter_by_total_l,
    coa_tot_count_pubs = prof_tot_count_pubs, 
    coa_tot_cited_by = prof_tot_cited_by,
    coa_tot_count_pubs_total = prof_tot_count_pubs_total_all,
    coa_tot_cited_by_total = prof_tot_cited_by_total_all,
    coa_tot_online_news = prof_tot_coa_attn_news_by,
    coa_tot_blogs = prof_tot_coa_attn_blog_by,
    coa_tot_twitter = prof_tot_coa_attn_twitter_by,
    coa_tot_online_news_total = prof_tot_coa_attn_news_by_total,
    coa_tot_blogs_total = prof_tot_coa_attn_blog_by_total,
    coa_tot_twitter_total = prof_tot_coa_attn_twitter_by_total,
    coa_tot_unique_m = prof_tot_unique_coa_m,
    coa_tot_unique_w = prof_tot_unique_coa_w,
    coa_tot_unique_u = prof_tot_unique_coa_u,
    coa_tot_count_pubs_l = prof_tot_count_pubs_l, 
    coa_tot_cited_by_l = prof_tot_cited_by_l,
    coa_tot_count_pubs_total_l = prof_tot_count_pubs_total_all_l,
    coa_tot_cited_by_total_l = prof_tot_cited_by_total_all_l,
    coa_tot_online_news_l = prof_tot_coa_attn_news_by_l,
    coa_tot_blogs_l = prof_tot_coa_attn_blog_by_l,
    coa_tot_twitter_l = prof_tot_coa_attn_twitter_by_l,
    coa_tot_online_news_total_l = prof_tot_coa_attn_news_by_total_l,
    coa_tot_blogs_total_l = prof_tot_coa_attn_blog_by_total_l,
    coa_tot_twitter_total_l = prof_tot_coa_attn_twitter_by_total_l,
    coa_tot_unique_m_l = prof_tot_unique_coa_m_l,
    coa_tot_unique_w_l = prof_tot_unique_coa_w_l,
    coa_tot_unique_u_l = prof_tot_unique_coa_u_l,
    news_national = lexis_national,
    news_regional = lexis_regional,
    news_intl = lexis_intl,
    news = lexis_all,
    news_national_total = lexis_national_total,
    news_regional_total = lexis_regional_total,
    news_intl_total = lexis_intl_total,
    news_total = lexis_all_total,
    news_national_l = lexis_national_l,
    news_regional_l = lexis_regional_l,
    news_intl_l = lexis_intl_l,
    news_l = lexis_all_l,
    news_national_total_l = lexis_national_total_l,
    news_regional_total_l = lexis_regional_total_l,
    news_intl_total_l = lexis_intl_total_l,
    news_total_l = lexis_all_total_l)
```
 
Select relevant columns and tidy everything up:
```{r}
prof_panel_tidy <- prof_panel_tidy %>%
  # but not 2024
  filter(year < 2024 & !is.na(year))

# tidy up mentions
prof_panel_tidy$online_news <- prof_panel_tidy$online_news + prof_panel_tidy$blogs
prof_panel_tidy$online_news_l <- prof_panel_tidy$online_news_l + prof_panel_tidy$blogs_l
prof_panel_tidy$online_news_total_l <- prof_panel_tidy$online_news_total_l + prof_panel_tidy$blogs_total_l

# coauthors this year
prof_panel_tidy$coa_online_news <- prof_panel_tidy$coa_online_news + prof_panel_tidy$coa_blogs
prof_panel_tidy$coa_online_news_l <- prof_panel_tidy$coa_online_news_l + prof_panel_tidy$coa_blogs_l
prof_panel_tidy$coa_online_news_total <- prof_panel_tidy$coa_online_news_total + prof_panel_tidy$coa_blogs_total
prof_panel_tidy$coa_online_news_total_l <- prof_panel_tidy$coa_online_news_total_l + prof_panel_tidy$coa_blogs_total_l

# all coauthors up until now
prof_panel_tidy$coa_tot_online_news <- prof_panel_tidy$coa_tot_online_news + prof_panel_tidy$coa_tot_blogs
prof_panel_tidy$coa_tot_online_news_l <- prof_panel_tidy$coa_tot_online_news_l + prof_panel_tidy$coa_tot_blogs_l
prof_panel_tidy$coa_tot_online_news_total <- prof_panel_tidy$coa_tot_online_news_total + prof_panel_tidy$coa_tot_blogs_total
prof_panel_tidy$coa_tot_online_news_total_l <- prof_panel_tidy$coa_tot_online_news_total_l + prof_panel_tidy$coa_tot_blogs_total_l

# get groups per years since entry
prof_panel_tidy$entry_batch <- cut(prof_panel_tidy$years_since_first_pub, breaks = seq(0, 50, by=10))
prof_panel_tidy$years_since_entry <- paste("up to", str_remove(str_split_i(as.character(prof_panel_tidy$entry_batch), ",", 2),"]"))
```

Alternatively, leave only those professors for whom we actually have lexis data:
```{r warning = F, message = F}
# ones we collected before 20.3. in the morning 
lexis_info <- file.info(list.files(path = "../lexis_crawl/downloads/zipfiles",
                                   pattern="*.zip",
                                   full.names = T))
lexis_rel_list <- filter(lexis_info,
                         mtime <= "2024-03-20 8:55:00")

lexis_rel_list$profile_id <- str_remove(str_remove(rownames(lexis_rel_list), "../lexis_crawl/downloads/zipfiles/"), ".zip")

# minus ones that are incomplete
missing_indices <- read_csv("../lexis_crawl/missing_indices.csv")

lexis_list <- filter(lexis_rel_list, ! profile_id %in% missing_indices$profile_id)

prof_panel_filter <- filter(prof_panel_tidy,
                            str_remove(profile_id, "https://www.narcis.nl/person/RecordID/") %in% lexis_list$profile_id)
```

# Simple descriptives

How many profs?
```{r}
length(unique(prof_panel_filter$profile_id))
```

Professors per field and subfield?
```{r}
print.data.frame(prof_panel_filter %>%
  distinct(profile_id, .keep_all = TRUE)%>%
  filter(!is.na(general_field))%>%
  group_by(general_field)%>%
  summarise(n = n())%>%
  arrange(-n))
```

## Correlations
A correlation matrix:
```{r}
round(cor(prof_panel_filter[c("count_pubs", "cited_by",
                              "online_news", "news", "twitter",
                              "coa_count_pubs", "coa_cited_by",
                              "coa_online_news", "coa_twitter")],
          use="complete.obs"), 2)
```

```{r}
round(cor(prof_panel_filter[c("count_pubs", "count_pubs_total_l",
                              "cited_by", "cited_by_total_all_l",
                              "online_news", "news", "twitter",
                              "coa_count_pubs", "coa_cited_by",
                              "coa_online_news", "coa_twitter")],
          use="complete.obs"), 2)
```
## VIFs

### News models
```{r}
test_vif <- plm(news~count_pubs + cited_by + inferred_gender + coa_tot_count_pubs_l +
                  coa_tot_cited_by_total_l + coa_online_news_total_l + coa_twitter_total_l + as.factor(general_field), 
                data = prof_panel_filter,
                model="pooling")
vif(test_vif)

test_vif <- plm(news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + coa_tot_count_pubs_l +
                  coa_tot_cited_by_total_l + coa_online_news_total_l + coa_twitter_total_l + as.factor(general_field), 
                data = prof_panel_filter,
                model="pooling")
vif(test_vif)
```
Online news
```{r}
test_vif <- plm(online_news~count_pubs + cited_by + inferred_gender + coa_tot_count_pubs_l +
                  coa_tot_cited_by_total_l + coa_online_news_total_l + coa_twitter_total_l + as.factor(general_field), 
                data = prof_panel_filter,
                model="pooling")
vif(test_vif)

test_vif <- plm(online_news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + coa_tot_count_pubs_l +
                  coa_tot_cited_by_total_l + coa_online_news_total_l + coa_twitter_total_l + as.factor(general_field), 
                data = prof_panel_filter,
                model="pooling")
vif(test_vif)
```
Twitter
```{r}
test_vif <- plm(twitter~count_pubs + cited_by + inferred_gender + coa_tot_count_pubs_l +
                  coa_tot_cited_by_total_l + coa_online_news_total_l + coa_twitter_total_l + as.factor(general_field), 
                data = prof_panel_filter,
                model="pooling")
vif(test_vif)

test_vif <- plm(twitter~count_pubs_total_l + cited_by_total_all_l + inferred_gender + coa_tot_count_pubs_l +
                  coa_tot_cited_by_total_l + coa_online_news_total_l + coa_twitter_total_l + as.factor(general_field), 
                data = prof_panel_filter,
                model="pooling")
vif(test_vif)
```
## Descriprives
And some descriptives:
```{r}
psych::describe(prof_panel_filter[c("count_pubs", "cited_by",
                              "online_news", "news", "twitter",
                              "coa_count_pubs", "coa_cited_by",
                              "coa_online_news", "coa_twitter")])
```

Get some panel statistics:
```{r}
xtsum::xtsum(
  prof_panel_filter,
  variables = c("count_pubs", "cited_by",
                "online_news", "news", "twitter",
                "coa_count_pubs", "coa_cited_by",
                "coa_online_news", "coa_twitter"),
  id = "profile_id",
  t = "year",
  na.rm = TRUE,
  return.data.frame = FALSE,
  dec = 2
)
```


# Big models

## Citations
```{r}
citations_full <- plm(cited_by ~ # professor publication variables
                  count_pubs_total_l + 
                  # gender
                  inferred_gender +
                  # attention variables
                  news_total_l + online_news_total_l + twitter_total_l +
                  # coauthor publication variables
                  coa_tot_count_pubs_l + coa_tot_cited_by_total_l +
                  # coauthor publication variables
                  coa_online_news_total_l + coa_twitter_total_l + 
                  # field and year controls
                  as.factor(general_field),
                 data = prof_panel_filter, model="pooling", index=c("profile_id", "year")) 

# clustered SE
coeftest(citations_full, vcov=vcovHC(citations_full,type="HC0",cluster="group"))


round(summary(citations_full)$r.squared,3)
```


## News

This time period's news given one's total citations/publications, past total 
attention, controlling for the field and year (Lexis sample only). Pooled model
with clustered SEs:
```{r}
news_full <- plm(news ~ # professor publication variables
                  count_pubs_total_l + cited_by_total_all_l + 
                  # gender
                  inferred_gender +
                  # attention variables
                  online_news_total_l + twitter_total_l +
                  # coauthor publication variables
                  coa_tot_count_pubs_l + coa_tot_cited_by_total_l +
                  # coauthor publication variables
                  coa_online_news_total_l + coa_twitter_total_l + 
                  # field and year controls
                  as.factor(general_field),
                 data = prof_panel_filter, model="pooling", index=c("profile_id", "year")) 

# clustered SE
coeftest(news_full, vcov=vcovHC(news_full,type="HC0",cluster="group"))


round(summary(news_full)$r.squared,3)
```
## Online news

This time period's online news given one's total citations/publications, past total 
attention, controlling for the field and year (Lexis sample only). Pooled model
with clustered SEs:
```{r}
online_news_full <- plm(online_news~ # professor publication variables
                  count_pubs_total_l + cited_by_total_all_l + 
                  # gender
                  inferred_gender +
                  # attention variables
                  news_total_l + twitter_total_l +
                  # coauthor publication variables
                  coa_tot_count_pubs_l + coa_tot_cited_by_total_l +
                  # coauthor publication variables
                  coa_online_news_total_l + coa_twitter_total_l + 
                  # field and year controls
                  as.factor(general_field),
                 data = prof_panel_filter, model="pooling", index=c("profile_id", "year")) 

# clustered SE
coeftest(online_news_full, vcov=vcovHC(online_news_full,type="HC0",cluster="group"))


round(summary(online_news_full)$r.squared,3)
```
## Twitter

This time period's twitter attention given one's total citations/publications, past total 
attention, controlling for the field and year (Lexis sample only). Pooled model
with clustered SEs:
```{r}
twitter_full <- plm(twitter~ # professor publication variables
                  count_pubs_total_l + cited_by_total_all_l + 
                  # gender
                  inferred_gender +
                  # attention variables
                  news_total_l + online_news_total_l +
                  # coauthor publication variables
                  coa_tot_count_pubs_l + coa_tot_cited_by_total_l +
                  # coauthor publication variables
                  coa_online_news_total_l + coa_twitter_total_l + 
                  # field and year controls
                  as.factor(general_field),
                 data = prof_panel_filter, model="pooling", index=c("profile_id", "year")) 

# clustered SE
coeftest(twitter_full, vcov=vcovHC(twitter_full,type="HC0",cluster="group"))


round(summary(twitter_full)$r.squared,3)
```

# Models A: Counts
## Only gender

Publications and gender:
```{r}
gender_pubs <- lm(count_pubs~inferred_gender, 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_pubs, vcov = vcovCL(gender_pubs, cluster = ~profile_id))
```
Citations and gender:
```{r}
gender_cits <- lm(cited_by~inferred_gender, 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_cits, vcov = vcovCL(gender_cits, cluster = ~profile_id))
```

Conventional news attention and gender:
```{r}
gender_online_news <- lm(news~inferred_gender, 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))
```

Online News attention and gender:
```{r}
gender_news <- lm(online_news~inferred_gender, 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))
```

Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~inferred_gender, 
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))
```

## Gender and fields

Reference:  "Arts & Humanities" 

Publications and gender:
```{r}
gender_pubs <- lm(count_pubs~inferred_gender+as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_pubs, vcov = vcovCL(gender_pubs, cluster = ~profile_id))
```
Citations and gender:
```{r}
gender_cits <- lm(cited_by~inferred_gender+as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_cits, vcov = vcovCL(gender_cits, cluster = ~profile_id))
```

Conventional news attention and gender:
```{r}
gender_online_news <- lm(news~inferred_gender+as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))
```
Online News attention and gender:
```{r}
gender_news <- lm(online_news~inferred_gender+as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))
```

Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~inferred_gender+as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))
```

## Gender and prof controls (not lagged)

News attention and gender:
```{r}
gender_news <- lm(news~count_pubs + cited_by + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Online news attention and gender:
```{r}
gender_online_news <- lm(online_news~count_pubs + cited_by + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))

summary(gender_online_news)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~count_pubs + cited_by + inferred_gender + as.factor(general_field),
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```


## Gender and prof controls (lagged)

### News 
News attention and gender:
```{r}
gender_news <- lm(news~count_pubs_l + cited_by_l + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```

Cumulative:

```{r}
gender_news <- lm(news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
### Online news
Online news attention and gender:
```{r}
gender_online_news <- lm(online_news~count_pubs_l + cited_by_l + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))

summary(gender_online_news)$adj.r.squared
```

Cumulative:
```{r}
gender_online_news <- lm(online_news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```

### Twitter
Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~count_pubs_l + cited_by_l + inferred_gender + as.factor(general_field),
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```

Cumulative:
```{r}
gender_twitter <- lm(twitter~count_pubs_total_l + cited_by_total_all_l + inferred_gender + as.factor(general_field),
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```

## Prof and coauathor controls

### Conventional news
News attention and gender:
```{r}
gender_news1 <- lm(news~count_pubs + cited_by + inferred_gender + coa_count_pubs +
                    coa_cited_by + coa_online_news + coa_twitter + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news1, vcov = vcovCL(gender_news1, cluster = ~profile_id))

summary(gender_news1)$adj.r.squared
```
Lagged controls:
```{r}
gender_news2 <- lm(news~count_pubs_l + cited_by_l + inferred_gender +
                    coa_count_pubs_l +
                    coa_cited_by_l + coa_online_news_l + coa_twitter_l + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news2, vcov = vcovCL(gender_news2, cluster = ~profile_id))

summary(gender_news2)$adj.r.squared
```
Coauthor totals:
```{r}
gender_news3 <- lm(news~count_pubs + cited_by + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news3, vcov = vcovCL(gender_news3, cluster = ~profile_id))

summary(gender_news3)$adj.r.squared
```

All totals:
```{r}
gender_news4 <- lm(news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news4, vcov = vcovCL(gender_news4, cluster = ~profile_id))

summary(gender_news4)$adj.r.squared
```


### Online news
News attention and gender:
```{r}
gender_online_news1 <- lm(online_news~count_pubs + cited_by + inferred_gender + coa_count_pubs +
                    coa_cited_by + coa_online_news + coa_twitter + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_online_news1, vcov = vcovCL(gender_online_news1, cluster = ~profile_id))

summary(gender_online_news1)$adj.r.squared
```
Lagged controls:
```{r}
gender_online_news2 <- lm(online_news~count_pubs_l + cited_by_l + inferred_gender +
                    coa_count_pubs_l +
                    coa_cited_by_l + coa_online_news_l + coa_twitter_l + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_online_news2, vcov = vcovCL(gender_online_news2, cluster = ~profile_id))

summary(gender_online_news2)$adj.r.squared
```
Coauthor totals:
```{r}
gender_online_news3 <- lm(online_news~count_pubs + cited_by + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_online_news3, vcov = vcovCL(gender_online_news3, cluster = ~profile_id))

summary(gender_online_news3)$adj.r.squared
```

All totals:
```{r}
gender_online_news4 <- lm(online_news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_online_news4, vcov = vcovCL(gender_online_news4, cluster = ~profile_id))

summary(gender_online_news4)$adj.r.squared
```

### Twitter
News attention and gender:
```{r}
gender_twitter1 <- lm(twitter~count_pubs + cited_by + inferred_gender + coa_count_pubs +
                    coa_cited_by + coa_online_news + coa_twitter + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_twitter1, vcov = vcovCL(gender_twitter1, cluster = ~profile_id))

summary(gender_twitter1)$adj.r.squared
```
Lagged controls:
```{r}
gender_twitter2 <- lm(twitter~count_pubs_l + cited_by_l + inferred_gender +
                    coa_count_pubs_l +
                    coa_cited_by_l + coa_online_news_l + coa_twitter_l + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_twitter2, vcov = vcovCL(gender_twitter2, cluster = ~profile_id))

summary(gender_twitter2)$adj.r.squared
```
Coauthor totals:
```{r}
gender_twitter3 <- lm(twitter~count_pubs + cited_by + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_twitter3, vcov = vcovCL(gender_twitter3, cluster = ~profile_id))

summary(gender_twitter3)$adj.r.squared
```

All totals:
```{r}
gender_twitter4 <- lm(twitter~count_pubs_total_l + cited_by_total_all_l + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_twitter4, vcov = vcovCL(gender_twitter4, cluster = ~profile_id))

summary(gender_twitter4)$adj.r.squared
```


## Cumulative media attention?

News attention and gender:
```{r}
gender_news <- lm(news~news_l + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Blog attention and gender:
```{r}
gender_online_news <- lm(blogs~blogs_l + as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))

summary(gender_online_news)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~twitter_l + as.factor(general_field),
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```

## Cumulative media attention, prof and coauthor controls
News attention and gender:
```{r}
gender_news <- lm(news~news_l + count_pubs + cited_by + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field) + as.factor(year), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Online news and gender:
```{r}
gender_online_news <- lm(online_news~online_news_l + count_pubs + cited_by + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field) + as.factor(year), 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))

summary(gender_online_news)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~twitter_l + count_pubs + cited_by + inferred_gender + coa_tot_count_pubs +
                    coa_tot_cited_by_total + coa_online_news_total + coa_twitter_total + as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```




## Cumulative media attention per gender?


News attention and gender:
```{r}
gender_news <- lm(news~news_l*inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id))

summary(gender_news)$adj.r.squared
```
Blog attention and gender:
```{r}
gender_online_news <- lm(online_news~online_news_l*inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter)

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id))

summary(gender_online_news)$adj.r.squared
```
Twitter attention and gender:
```{r}
gender_twitter <- lm(twitter~twitter_l*inferred_gender + as.factor(general_field) +years_since_first_pub*inferred_gender,
                  data = prof_panel_filter)

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id))

summary(gender_twitter)$adj.r.squared
```



the model above, watching out for totals etc. 
+ 
 
Network
- coauthors 
- coauthors cites
- coauthors attention
- are these for t or t-1

Share of coauthors in the high end of attention distribution.


- any attention (are you in the attention elite)
- amount of attention
- top 10%

PUB TYPE
- articles, books + book chapters
- preprints? conf. proceedings?



# Models B: Any attention

Get a binary variable denoting whether professor has gotten any attention this year:

```{r}
prof_panel_filter$any_news <- as.factor(ifelse(prof_panel_filter$news > 0, 1, 0))
prof_panel_filter$any_news_l <- as.factor(ifelse(prof_panel_filter$news_l > 0, 1, 0))

prof_panel_filter$any_online_news <- as.factor(ifelse(prof_panel_filter$online_news > 0, 1, 0))
prof_panel_filter$any_online_news_l <- as.factor(ifelse(prof_panel_filter$online_news_l > 0, 1, 0))

prof_panel_filter$any_twitter <- as.factor(ifelse(prof_panel_filter$twitter > 0, 1, 0))
prof_panel_filter$any_twitter_l <- as.factor(ifelse(prof_panel_filter$twitter_l > 0, 1, 0))
```

## Gender and prof controls
News attention and gender:
```{r}
gender_news <- glm(any_news~count_pubs + cited_by + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter,
                  family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(any_online_news~count_pubs + cited_by + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter,
                  family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(any_twitter~count_pubs + cited_by + inferred_gender + as.factor(general_field),
                  data = prof_panel_filter,
                  family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```



## Gender, prof, and coauthor controls
News attention and gender:
```{r}
gender_news <- glm(any_news~count_pubs + cited_by + inferred_gender + 
                     coa_tot_count_pubs + coa_tot_cited_by_total + 
                     coa_online_news_total + coa_twitter_total +
                     as.factor(general_field), 
                   data = prof_panel_filter,
                   family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(any_online_news~count_pubs + cited_by + inferred_gender + 
                            coa_tot_count_pubs + coa_tot_cited_by_total + 
                            coa_online_news_total + coa_twitter_total +
                            as.factor(general_field), 
                          data = prof_panel_filter,
                          family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(any_twitter~count_pubs + cited_by + inferred_gender + 
                        coa_tot_count_pubs + coa_tot_cited_by_total + 
                        coa_online_news_total + coa_twitter_total +
                        as.factor(general_field), 
                      data = prof_panel_filter,
                      family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```




# Models C: Top 5% of attention

Get a binary variable denoting whether professor has been in the top 5% of the attention
for this source this year in their field:
```{r}
panel_filter_long <- prof_panel_filter %>%
  pivot_longer(online_news:news, names_to = "measure", values_to = "value")

top_5_attn <- panel_filter_long %>%
  filter(!is.na(general_field) & !is.na(year) & year > 2011)%>%
  group_by(general_field, year, measure)%>%
  filter(quantile(value, 0.95, na.rm = TRUE)<value)%>%
  select(profile_id, general_field, year, measure, value)

top_5_attn$measure <- paste0(top_5_attn$measure, "_top_5")
# top_5_attn$value <- 1

top_5_attn <- top_5_attn %>%
  pivot_wider(names_from = "measure")%>%
  mutate(across(contains('top_5'),  ~ifelse(is.na(.), 0, 1)))

prof_panel_filter_top <- merge(prof_panel_filter,
                               top_5_attn[c("year", "profile_id", "general_field", "news_top_5", "online_news_top_5", "twitter_top_5")],
                               by = c("profile_id", "year", "general_field"),
                               all.x = TRUE,
                               all.y = FALSE)
```

## Gender and prof controls

### This time period
News attention and gender:
```{r}
gender_news <- glm(news_top_5~count_pubs + cited_by + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter_top,
                  family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(online_news_top_5~count_pubs + cited_by + inferred_gender + as.factor(general_field), 
                  data = prof_panel_filter_top,
                  family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(twitter_top_5~count_pubs + cited_by + inferred_gender + as.factor(general_field),
                  data = prof_panel_filter_top,
                  family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```

### Lag

News attention and gender:
```{r}
gender_news <- glm(news_top_5~count_pubs_l + cited_by_l + inferred_gender + 
                     coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                     coa_online_news_total_l + coa_twitter_total_l +
                     as.factor(general_field), 
                   data = prof_panel_filter_top,
                   family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(online_news_top_5~count_pubs_l + cited_by_l + inferred_gender + 
                            coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                            coa_online_news_total_l + coa_twitter_total_l +
                            as.factor(general_field), 
                          data = prof_panel_filter_top,
                          family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(twitter_top_5~count_pubs_l + cited_by_l + inferred_gender + 
                        coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                        coa_online_news_total_l + coa_twitter_total_l +
                        as.factor(general_field), 
                      data = prof_panel_filter_top,
                      family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```

### Totals
News attention and gender:
```{r}
gender_news <- glm(news_top_5~count_pubs_total_l + cited_by_total_all_l + inferred_gender + 
                     coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                     coa_online_news_total_l + coa_twitter_total_l +
                     as.factor(general_field), 
                   data = prof_panel_filter_top,
                   family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(online_news_top_5~count_pubs_total_l + cited_by_total_all_l + inferred_gender + 
                            coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                            coa_online_news_total_l + coa_twitter_total_l +
                            as.factor(general_field), 
                          data = prof_panel_filter_top,
                          family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(twitter_top_5~count_pubs_total_l + cited_by_total_all_l + inferred_gender + 
                        coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                        coa_online_news_total_l + coa_twitter_total_l +
                        as.factor(general_field), 
                      data = prof_panel_filter_top,
                      family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```



## Gender, prof, and coauthor controls

### This time period:

News attention and gender:
```{r}
gender_news <- glm(any_news~count_pubs + cited_by + inferred_gender + 
                     coa_tot_count_pubs + coa_tot_cited_by_total + 
                     coa_online_news_total + coa_twitter_total +
                     as.factor(general_field), 
                   data = prof_panel_filter,
                   family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(any_online_news~count_pubs + cited_by + inferred_gender + 
                            coa_tot_count_pubs + coa_tot_cited_by_total + 
                            coa_online_news_total + coa_twitter_total +
                            as.factor(general_field), 
                          data = prof_panel_filter,
                          family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(any_twitter~count_pubs + cited_by + inferred_gender + 
                        coa_tot_count_pubs + coa_tot_cited_by_total + 
                        coa_online_news_total + coa_twitter_total +
                        as.factor(general_field), 
                      data = prof_panel_filter,
                      family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```

### Lag

News attention and gender:
```{r}
gender_news <- glm(any_news~count_pubs_l + cited_by_l + inferred_gender + 
                     coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                     coa_online_news_total_l + coa_twitter_total_l +
                     as.factor(general_field), 
                   data = prof_panel_filter,
                   family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(any_online_news~count_pubs_l + cited_by_l + inferred_gender + 
                            coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                            coa_online_news_total_l + coa_twitter_total_l +
                            as.factor(general_field), 
                          data = prof_panel_filter,
                          family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(any_twitter~count_pubs_l + cited_by_l + inferred_gender + 
                        coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                        coa_online_news_total_l + coa_twitter_total_l +
                        as.factor(general_field), 
                      data = prof_panel_filter,
                      family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```

### Totals
News attention and gender:
```{r}
gender_news <- glm(any_news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + 
                     coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                     coa_online_news_total_l + coa_twitter_total_l +
                     as.factor(general_field), 
                   data = prof_panel_filter,
                   family = "binomial")

# clustered SE
coeftest(gender_news, vcov = vcovCL(gender_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_news)
```
Online news attention and gender:
```{r}
gender_online_news <- glm(any_online_news~count_pubs_total_l + cited_by_total_all_l + inferred_gender + 
                            coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                            coa_online_news_total_l + coa_twitter_total_l +
                            as.factor(general_field), 
                          data = prof_panel_filter,
                          family = "binomial")

coeftest(gender_online_news, vcov = vcovCL(gender_online_news, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_online_news)
```
Twitter attention and gender:
```{r}
gender_twitter <- glm(any_twitter~count_pubs_total_l + cited_by_total_all_l + inferred_gender + 
                        coa_tot_count_pubs_l + coa_tot_cited_by_total_l + 
                        coa_online_news_total_l + coa_twitter_total_l +
                        as.factor(general_field), 
                      data = prof_panel_filter,
                      family = "binomial")

coeftest(gender_twitter, vcov = vcovCL(gender_twitter, cluster = ~profile_id, type = "HC0"))

PseudoR2(gender_twitter)
```



